---
title: "SB R2 SIMMAP_ACE - All Primates - 062522 v1"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
All Primates Analysis

Run: SIMMAPS ACE 062522 v1
	Testing revised data from R2 but running original fitMk program, not parallel
	Gorilla g in strict classification is folivore
	Predictors:
		Fol.Non.Fol.Strict
		Fol.Non.Fol.Per
		Frug.Non.Frug.Per
		Social.System.DRclass
		Social.System.DGT
		Mating.System
		Activity.Period.DN
		GSC >50

	
```{r}
rm(list=ls())

####CHANGE
#Latest run
load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAPS/Univariate/WS SIMMAP Only - Univariate 062822.RData")


library(phytools)
#devtools::install_github("kopperud/slouch",force=TRUE)

library(slouch)
library(ggsci)
library(treeplyr)
#library(bayou)
library(plyr)
#library(ape)
#library(viridis)
options(scipen=999)
library(parallel)

```


```{r}
#Just mating system
#reg.colors<-pal_npg()(length(unique(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN))))

#Mating system Only
#regimes<-c(as.character(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),as.character(internal.regimes.FoDCS.ssgt.ap))
#edge.regimes <- factor(regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])
#print(edge.regimes)
#print(reg.colors)
#plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge.regimes], edge.width = 1.75, cex = 0.00001)
#6X4 PDF
```


```{r}
#library(ggsci)

#Just mating system
#reg.colors<-pal_npg()(length(unique(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)))
#reg.colors<-pal_aaas()(length(unique(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)))

#Mating system Only
#regimes<-c(as.character(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System),as.character(internal.regimes.ms))
#edge.regimes <- factor(regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])
#print(edge.regimes)
##print(reg.colors)
#plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge.regimes], edge.width = 1.75, cex = 0.00001)
#6X4 PDF
```


Summarize SIMMAP Discrete Character Mappings based on highest posterior probabilities with Activity Period
```{r}
## Extract the most likely regime for each internal node
## These have order n+1, n+2, n+3 ...
#internal_regimes_gs <- apply(reconstruction.gs$ace, #
#                               #1, 
#                               #function(e) colnames(reconstruction.gs$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS<-summary(reconstruction.FoDCS)

internal.regimes.FoDCS<- apply(reconstruction.FoDCS$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDC<-summary(reconstruction.FoDC)

internal.regimes.FoDC<- apply(reconstruction.FoDC$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC$ace)[which.max(e)])



#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC<-summary(reconstruction.FrDC)

internal.regimes.FrDC<- apply(reconstruction.FrDC$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC$ace)[which.max(e)])

########
reconstruction.ssgt<-summary(reconstruction.ssgt)
internal.regimes.ssgt <- apply(reconstruction.ssgt$ace, 
                               1, 
                               function(e) colnames(reconstruction.ssgt$ace)[which.max(e)])

########
reconstruction.ss<-summary(reconstruction.ss)
internal.regimes.ss <- apply(reconstruction.ss$ace, 
                               1, 
                               function(e) colnames(reconstruction.ss$ace)[which.max(e)])
################
reconstruction.ms<-summary(reconstruction.ms)
internal.regimes.ms <- apply(reconstruction.ms$ace, 
                               1, 
                               function(e) colnames(reconstruction.ms$ace)[which.max(e)])

#########
#Frugivore Diet Categories, Activity Pattern
reconstruction.gsc<-summary(reconstruction.gsc)
internal.regimes.gsc <- apply(reconstruction.gsc$ace, 
                               1, 
                               function(e) colnames(reconstruction.gsc$ace)[which.max(e)])


###############
reconstruction.ap<-summary(reconstruction.ap)
internal.regimes.ap <- apply(reconstruction.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.ap$ace)[which.max(e)])

```


Single Factors
```{r}
##############
#Frugivore Diet Categories
BrBo.diet.trdata$phy$node.label <- internal.regimes.FrDC

  ECV.FrDC.BoM.OUDF<-slouch.fit(BrBo.diet.trdata$phy,
                     species = BrBo.diet.trdata$phy$tip.label,
                     response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.diet.trdata$dat$Frug.Non.Frug.Per ,
                     direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.diet.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FrDC.BoM.OUDF)

ECV.FrDC.BoM.BM<-brown.fit(BrBo.diet.trdata$phy,
                     species = BrBo.diet.trdata$phy$tip.label,
                     response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.diet.trdata$dat$Frug.Non.Frug.Per ,
                    direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.diet.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FrDC.BoM.BM)


#OU Model of Evolution
ECV.BoM.FrDC.OU<-slouch.fit(phy = BrBo.diet.trdata$phy,
                              species = BrBo.diet.trdata$phy$tip.label,
                              response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.diet.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.0001, 0.0001))

summary(ECV.BoM.FrDC.OU)


#BM Model of Evolution
ECV.BoM.FrDC.BM<-brown.fit(phy = BrBo.diet.trdata$phy,
                              species = BrBo.diet.trdata$phy$tip.label,
                              response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.diet.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.0001, 0.0001))


summary(ECV.BoM.FrDC.BM)


```


```{r}
##############
#Folivore Diet Categories
BrBo.diet.trdata$phy$node.label <- internal.regimes.FoDCS

  ECV.FoDCS.BoM.OUDF<-slouch.fit(BrBo.diet.trdata$phy,
                     species = BrBo.diet.trdata$phy$tip.label,
                     response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.diet.trdata$dat$Fol.Non.Fol.Strict,
                     direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.diet.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.BoM.OUDF)

  ECV.FoDCS.BoM.BM<-brown.fit(BrBo.diet.trdata$phy,
                     species = BrBo.diet.trdata$phy$tip.label,
                     response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.diet.trdata$dat$Fol.Non.Fol.Strict ,
                    direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.diet.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.BoM.BM)

```

```{r}
##############
#Folivore Diet Categories
BrBo.diet.trdata$phy$node.label <- internal.regimes.FoDC

  ECV.FoDC.BoM.OUDF<-slouch.fit(BrBo.diet.trdata$phy,
                     species = BrBo.diet.trdata$phy$tip.label,
                     response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.diet.trdata$dat$Fol.Non.Fol.Per,
                     direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.diet.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.BoM.OUDF)

  ECV.FoDC.BoM.BM<-brown.fit(BrBo.diet.trdata$phy,
                     species = BrBo.diet.trdata$phy$tip.label,
                     response = log(BrBo.diet.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.diet.trdata$dat$Fol.Non.Fol.Per ,
                    direct.cov = log(BrBo.diet.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.diet.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.diet.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.BoM.BM)

```

Continuous Factors
```{r}
############
#Group Size Continuous

ECV.GS.BoM.OURD<-slouch.fit(BrBo.GS.trdata$phy,
                     species = BrBo.GS.trdata$phy$tip.label,
                     response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.GS.trdata$dat$Combo.AGS),
                     direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.GS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                     hl_values = seq(0.001, max.hl*3, length.out = 50),
                     vy_values = seq(0.001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.BoM.OURD)

ECV.GS.BoM.BM<-brown.fit(BrBo.GS.trdata$phy,
                     species = BrBo.GS.trdata$phy$tip.label,
                     response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.GS.trdata$dat$Combo.AGS),
                    direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.GS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.BoM.BM)

######################


#OU Model of Evolution
ECV.BoM.GS.OU<-slouch.fit(phy = BrBo.GS.trdata$phy,
                              species = BrBo.GS.trdata$phy$tip.label,
                              response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.GS.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.0001, 0.0001))

summary(ECV.BoM.GS.OU)


#BM Model of Evolution
ECV.BoM.GS.BM<-brown.fit(phy = BrBo.GS.trdata$phy,
                              species = BrBo.GS.trdata$phy$tip.label,
                              response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.GS.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.0001, 0.0001))


summary(ECV.BoM.GS.BM)

```

Activity Pattern
```{r}
###########
BrBo.GS.trdata$phy$node.label <- internal.regimes.ap

  ECV.AP.BoM.OUDF<-slouch.fit(BrBo.GS.trdata$phy,
                     species = BrBo.GS.trdata$phy$tip.label,
                     response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.GS.trdata$dat$Activity.Period.DN,
                     direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.GS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.AP.BoM.OUDF)



  ECV.AP.BoM.BM<-brown.fit(BrBo.GS.trdata$phy,
                     species = BrBo.GS.trdata$phy$tip.label,
                     response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.GS.trdata$dat$Activity.Period.DN,
                    direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.GS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.AP.BoM.BM)



```


Group Size
```{r}
###########
#Group Size Categories
BrBo.GS.trdata$phy$node.label <- internal.regimes.gsc

  ECV.GSC.BoM.OUDF<-slouch.fit(BrBo.GS.trdata$phy,
                     species = BrBo.GS.trdata$phy$tip.label,
                     response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.GS.trdata$dat$Cat.group.size,
                     direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.GS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GSC.BoM.OUDF)


  ECV.GSC.BoM.BM<-brown.fit(BrBo.GS.trdata$phy,
                     species = BrBo.GS.trdata$phy$tip.label,
                     response = log(BrBo.GS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.GS.trdata$dat$Cat.group.size,
                    direct.cov = log(BrBo.GS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.GS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.GS.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GSC.BoM.BM)



```


```{r}
###########
#Social System GT
BrBo.SS.trdata$phy$node.label <- internal.regimes.ssgt

  ECV.SSGT.BoM.OUDF<-slouch.fit(BrBo.SS.trdata$phy,
                     species = BrBo.SS.trdata$phy$tip.label,
                     response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.SS.trdata$dat$Social.System.DGT,
                     direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.SS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SSGT.BoM.OUDF)


  ECV.SSGT.BoM.BM<-brown.fit(BrBo.SS.trdata$phy,
                     species = BrBo.SS.trdata$phy$tip.label,
                     response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.SS.trdata$dat$Social.System.DGT,
                    direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.SS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SSGT.BoM.BM)
###########
#Social System
BrBo.SS.trdata$phy$node.label <- internal.regimes.ss

  ECV.SS.BoM.OUDF<-slouch.fit(BrBo.SS.trdata$phy,
                     species = BrBo.SS.trdata$phy$tip.label,
                     response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.SS.trdata$dat$Social.System.DRclass,
                     direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.SS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SS.BoM.OUDF)


  ECV.SS.BoM.BM<-brown.fit(BrBo.SS.trdata$phy,
                     species = BrBo.SS.trdata$phy$tip.label,
                     response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.SS.trdata$dat$Social.System.DRclass,
                    direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.SS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SS.BoM.BM)


###########
#Mating System
BrBo.SS.trdata$phy$node.label <- internal.regimes.ms

  ECV.MS.BoM.OUDF<-slouch.fit(BrBo.SS.trdata$phy,
                     species = BrBo.SS.trdata$phy$tip.label,
                     response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.SS.trdata$dat$Mating.System,
                     direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.SS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.MS.BoM.OUDF)


  ECV.MS.BoM.BM<-brown.fit(BrBo.SS.trdata$phy,
                     species = BrBo.SS.trdata$phy$tip.label,
                     response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.SS.trdata$dat$Mating.System,
                    direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.SS.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.MS.BoM.BM)



#OU Model of Evolution
ECV.BoM.SS.OU<-slouch.fit(phy = BrBo.SS.trdata$phy,
                              species = BrBo.SS.trdata$phy$tip.label,
                              response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.SS.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.0001, 0.0001))

summary(ECV.BoM.SS.OU)


#BM Model of Evolution
ECV.BoM.SS.BM<-brown.fit(phy = BrBo.SS.trdata$phy,
                              species = BrBo.SS.trdata$phy$tip.label,
                              response = log(BrBo.SS.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.SS.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.SS.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.SS.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.0001, 0.0001))


summary(ECV.BoM.SS.BM)

```




```{r}
#save.image("WS from SIMMAPACE-All Primates - Slouch pt 3.RData")
```



```{r}

#Single factors in addition to Body Mass
#############################
slouch.output<-make.slouch.table(ECV.FoDCS.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict",dim(BrBo.diet.trdata$dat)[1])
slouch.output<-make.slouch.table(ECV.FoDCS.BoM.BM,"FF.BM","Fol Diet Categories Strict",dim(BrBo.diet.trdata$dat)[1],slouch.output)


#############################
slouch.output<-make.slouch.table(ECV.FoDC.BoM.OUDF,"OU.FF.DE","Fol Diet Categories",dim(BrBo.diet.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.BoM.BM,"FF.BM","Fol Diet Categories",dim(BrBo.diet.trdata$dat)[1],slouch.output)


#Single factors in addition to Body Mass
#############################
slouch.output<-make.slouch.table(ECV.FrDC.BoM.OUDF,"OU.FF.DE","Frug Diet Categories",dim(BrBo.diet.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.BoM.BM,"FF.BM","Frug Diet Categories",dim(BrBo.diet.trdata$dat)[1],slouch.output)

slouch.output<-make.slouch.table(ECV.BoM.FrDC.OU,"OU.DE","Comparison-Body Mass",dim(BrBo.diet.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.BoM.FrDC.BM,"BM","Comparison-Body Mass",dim(BrBo.diet.trdata$dat)[1],slouch.output)


#############################
slouch.output<-make.slouch.table(ECV.GSC.BoM.OUDF,"OU.FF.DE","Group Size Categories",dim(BrBo.GS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GSC.BoM.BM,"FF.BM","Group Size Categories",dim(BrBo.GS.trdata$dat)[1],slouch.output)

###########
slouch.output<-make.slouch.table(ECV.GS.BoM.OURD,"OU.AD.DE","Group Size",dim(BrBo.GS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.BoM.BM,"BM","Group Size",dim(BrBo.GS.trdata$dat)[1],slouch.output)
###########


#############################
slouch.output<-make.slouch.table(ECV.AP.BoM.OUDF,"OU.FF.DE","Activity Pattern",dim(BrBo.GS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.AP.BoM.BM,"FF.BM","Activity Pattern",dim(BrBo.GS.trdata$dat)[1],slouch.output)


slouch.output<-make.slouch.table(ECV.BoM.GS.OU,"OU.DE","Comparison-Body Mass",dim(BrBo.GS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.BoM.GS.BM,"BM","Comparison-Body Mass",dim(BrBo.GS.trdata$dat)[1],slouch.output)


#############################
slouch.output<-make.slouch.table(ECV.SSGT.BoM.OUDF,"OU.FF.DE","Social System GT",dim(BrBo.SS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.SSGT.BoM.BM,"FF.BM","Social System GT",dim(BrBo.SS.trdata$dat)[1],slouch.output)


#############################
slouch.output<-make.slouch.table(ECV.SS.BoM.OUDF,"OU.FF.DE","Social System",dim(BrBo.SS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.SS.BoM.BM,"FF.BM","Social System",dim(BrBo.SS.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.MS.BoM.OUDF,"OU.FF.DE","Mating System",dim(BrBo.SS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.MS.BoM.BM,"FF.BM","Mating System",dim(BrBo.SS.trdata$dat)[1],slouch.output)

slouch.output<-make.slouch.table(ECV.BoM.SS.OU,"OU.DE","Comparison-Body Mass",dim(BrBo.SS.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.BoM.SS.BM,"BM","Comparison-Body Mass",dim(BrBo.SS.trdata$dat)[1],slouch.output)


slouch.table<-make_regression_table(slouch.output)

```

```{r}
save.image("SBR2 - WS from SIMMAP ACE - All Primates - 128 sp - Univariate 062822.RData")
```


```{r}
write.table(slouch.output,"SBR2_SIMMAPACE_All_Primates_Scaled_Slouch_Table_128sp_Univariate_062822.csv",sep=",",row.names=FALSE)
write.table(slouch.table,"SBR2_SIMMAPACE_All_Primates_Scaled_AIC_Table_128sp_Univariate_062822.csv",sep=",",row.names=FALSE)
```

``

 