---
title: "SBR2 - BDS ms All Primates Make SIMMAPs Code - Univariate - 062722 v1"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
All Primates Analysis

Run: SIMMAPS 062722 v1
	Testing revised data from R2 but running original fitMk program, not parallel
	Gorilla g in strict classification is folivore
	Predictors:
		Fol.Non.Fol.Strict
		Fol.Non.Fol.Per
		Frug.Non.Frug.Per
		Social.System.DRclass
		Social.System.DGT
		Mating.System
		Activity.Period.DN
		GSC >50

```{r}

rm(list=ls())
#setDefaultCluster(cl=NULL); stopCluster(cl) 

closeAllConnections()

#devtools::install_github("kopperud/slouch")
library(slouch)

#devtools::install_github("liamrevell/phytools")
library(treeplyr)
library(phytools)
library(optimParallel)

#library(bayou)
#library(plyr)
#library(ape)
#library(viridis)
options(scipen=999)

#For execution on a local, multicore CPU with excess RAM we recommend calling
#options(mc.cores = parallel::detectCores()-2)

#Load programs written for R1
source("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.slouch.simmap.table.v1.R")

source("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.slouch.simmap.AIC.table.R1.v1.R")

source("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.regression.table.R1.R")

source("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.slouch.table.R1.v1.R")

#source("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/Programs/fitMk.parallel.LR.R")

```

Read in all data, including data on brain and body size with measurement error from Grabowski et al. (2016)

```{r}
#Orignal submission tree
#phylo.tree<-read.tree("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/Tree/AAPA_111118_10K.tre")

#SB Revision 1 Tree
phylo.tree<-read.tree("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Tree/SB_Rv1_10K.tre")

#After renaming family to Callitrichidae - only change
brbo.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/ME Data/BrBo_means_predME_10192020_Callitri_tarsiers_step.csv")


#diet.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/My Diet Data/Primate_Diet_Breakdown_051222.csv") #052122 Runs Data

diet.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/My Diet Data/Primate_Diet_Breakdown_062522.csv")

avg_GS.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New Group Size Data/ActPeriod GroupSize Data 050822.csv")

#avg_GS.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New Group Size Data/Average.GS.DeCasien.Powell.01232019.csv")

#SS.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New SS Data/DeCasien MG Latest SS 041422.csv")

SS.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New SS Data/Sociality Dataset 061022.csv")


```

Drop tip for Chiropotes satanas to match original submission sample
```{r}
#which(phylo.tree$tip.label=="Chiropotes_satanas")
#length(phylo.tree$tip.label)
#phylo.tree<-drop.tip(phylo.tree,tip="Chiropotes_satanas")
#length(phylo.tree$tip.label)
```


Drop tip for Callimico_goeldii to match R1 submission
```{r}
which(phylo.tree$tip.label=="Callimico_goeldii")
length(phylo.tree$tip.label)
phylo.tree<-drop.tip(phylo.tree,tip="Callimico_goeldii")
length(phylo.tree$tip.label)

```


Rescale to unit length
```{r}
l.tree<-max(branching.times(phylo.tree))
phylo.tree$edge.length<-phylo.tree$edge.length/l.tree ## rescale tree to height 1
max(branching.times(phylo.tree))

```


Get tree length
```{r}
phylo.tree <- multi2di(phylo.tree, random=FALSE)
phylo.tree$edge.length[phylo.tree$edge.length==0] <- .Machine$double.eps

#Reorder tree "postorder" to match bayou
#phylo.tree<-reorder(phylo.tree,order = "postorder")
max(branching.times(phylo.tree))
```


Add on measurement error columns for Brain and Body Size
```{r}
#Brain/Body/Diet Data
brbo.data$N.species

brbo.data<-mutate(brbo.data,me.ECV.species=brbo.data$predict.sp.ln_ECV/brbo.data$N.species)
brbo.data<-mutate(brbo.data,me.BoM.species=brbo.data$predict.sp.ln_Body.mass/brbo.data$N.body.mass.species)

brbo.data<-mutate(brbo.data,me.ECV.females=brbo.data$predict.F.ln_ECV/brbo.data$N.female)
brbo.data<-mutate(brbo.data,me.BoM.females=brbo.data$predict.F.ln_Body.mass/brbo.data$N.body.mass.female)

brbo.data<-mutate(brbo.data,me.ECV.males=brbo.data$predict.M.ln_ECV/brbo.data$N.male)
brbo.data<-mutate(brbo.data,me.BoM.males=brbo.data$predict.M.ln_Body.mass/brbo.data$N.body.mass.male)
```
Split into Haplorhinnes vs. Strepsirrhines
```{r}
#brbo.data<-filter(brbo.data,Suborder=="Haplorrhini")
#brbo.data<-filter(brbo.data,Suborder=="Strepsirrhini")
#brbo.data<-filter(brbo.data,Parvorder=="Catarrhini")
#brbo.data<-filter(brbo.data,Parvorder=="Platyrrhini")

```


Max vy for body mass - add in upper range for vy
```{r}
#3* Variance of logged response is good upper range for vy says Kjetil, but too much in this case
max.vy<-var(log(brbo.data$Body.mass.species.mean),na.rm=TRUE)
max.hl<-max(branching.times(phylo.tree))
```

Diet Data, independently
```{r}
#Frug/Non Frug, Fol/Non Fol Diet Category Data
BrBo.diet.data<-merge(brbo.data,diet.data,by="Genus_Species")
dim(BrBo.diet.data)

BrBo.diet.trdata <- make.treedata(phylo.tree, BrBo.diet.data,name_column="Genus_Species")
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean)&!is.na(Frug.Non.Frug.Per))

BrBo.diet.trdata<-filter(BrBo.diet.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean))

BrBo.diet.trdata<-filter(BrBo.diet.trdata,!is.na(Fol.Non.Fol.Per))

dim(BrBo.diet.trdata$dat)

#For original file with non-substuted males/females for species means
BrBo.diet.trdata<-filter(BrBo.diet.trdata, N.male>=1 & N.body.mass.male>=1 & N.female>=1 & N.body.mass.female>=1 & N.species>1 & N.body.mass.species>1)
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,N.species!="NA" & N.body.mass.species!="NA")

#BrBo.diet.trdata<-filter(BrBo.diet.trdata, N.species>=1 & N.body.mass.species>=1)
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,N.species!="NA" & N.body.mass.species!="NA")

dim(BrBo.diet.trdata$dat)

#write.table(BrBo.diet.trdata$dat,"test.csv",sep=",",row.names = FALSE)

#BrBo.diet.trdata$dat$Fol.Non.Fol.Per<-revalue(BrBo.diet.trdata$dat$Fol.Non.Fol.Per,c("Fol"="Folivorous","Non.Fol"="Non"))

#BrBo.diet.trdata$dat$Frug.Non.Frug.Per<-revalue(BrBo.diet.trdata$dat$Frug.Non.Frug.Per,c("Frug"="Frugivorous","Non.Frug"="Non"))

```

Sociality Data
```{r}
#Frug/Non Frug, Fol/Non Fol Diet Category Data
BrBo.SS.data<-merge(brbo.data,SS.data,by="Genus_Species")
dim(BrBo.SS.data)

BrBo.SS.trdata <- make.treedata(phylo.tree, BrBo.SS.data,name_column="Genus_Species")

BrBo.SS.trdata<-filter(BrBo.SS.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean))

BrBo.SS.trdata<-filter(BrBo.SS.trdata,!is.na(Social.System.DRclass))

dim(BrBo.SS.trdata$dat)

#For original file with non-substuted males/females for species means
BrBo.SS.trdata<-filter(BrBo.SS.trdata, N.male>=1 & N.body.mass.male>=1 & N.female>=1 & N.body.mass.female>=1 & N.species>1 & N.body.mass.species>1)

dim(BrBo.SS.trdata$dat)

#write.table(BrBo.diet.trdata$dat,"test.csv",sep=",",row.names = FALSE)

```

Group Size and Activity Period Data
```{r}
#Frug/Non Frug, Fol/Non Fol Diet Category Data
BrBo.GS.data<-merge(brbo.data,avg_GS.data,by="Genus_Species")
dim(BrBo.GS.data)

BrBo.GS.trdata <- make.treedata(phylo.tree, BrBo.GS.data,name_column="Genus_Species")

BrBo.GS.trdata<-filter(BrBo.GS.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean))
BrBo.GS.trdata<-filter(BrBo.GS.trdata,!is.na(Combo.AGS))

dim(BrBo.GS.trdata$dat)

#For original file with non-substuted males/females for species means
BrBo.GS.trdata<-filter(BrBo.GS.trdata, N.male>=1 & N.body.mass.male>=1 & N.female>=1 & N.body.mass.female>=1 & N.species>1 & N.body.mass.species>1)

dim(BrBo.GS.trdata$dat)


```


Break average group size continuous variable into categories
```{r}
#################
library(ape)

#Group size into 
gs.cat<-cut(BrBo.GS.trdata$dat$Combo.AGS,
    #breaks = c(0,5, 10, 25, Inf), 
    #labels = c("1-5","6-10","11-25",">25"), 
    breaks = c(0,5, 10, 25, 50,Inf), 
    labels = c("1-5","6-10","11-25","26-50",">50"), 
    right = FALSE)

BrBo.GS.trdata$dat$Cat.group.size<-gs.cat
```

Simmap Setup
```{r}
sim.num<-25 #25
loops.num<-2 #2
```



Now use SIMMAP to reconstruct social system, group size, for painting on trees  
```{r}
#Setup dataset for info on model fits
saved.discrete.models<-data.frame("Model"=NA,"AIC ER"=NA,"AIC SYM"=NA,"AIC ARD"=NA)
```

# Make SIMMAPs


```{r}
#cl = makeCluster(parallel::detectCores()-2) 
#cl<-parallel::detectCores()-2 #Cl for fitMk function
num.cores=parallel::detectCores()-2 #For mclapply function

########################
#Social System GT
#reconstruction.ssgt <- ace(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT), BrBo.Diet.DC.GS.SS.AP.trdata$phy, type = "d")

reconstruction.ssgt <- as.vector(BrBo.SS.trdata$dat$Social.System.DGT)
names(reconstruction.ssgt)<-BrBo.SS.trdata$phy$tip.label
#reconstruction.ssgt<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.ssgt,model="ER",Q="empirical",nsim=sim.num)   
tree<-BrBo.SS.trdata$phy
x<-reconstruction.ssgt

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.SS.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.SS.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.SS.trdata$phy,x,model="ARD")
saved.discrete.models<-rbind(saved.discrete.models,c("SSGT",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))
test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]

fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states
trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.ssgt<-trees


```
                                                                                                                                      Strict Folivore Definition
```{r}
########################
#Fol.Non.Fol.Strict Diet Categories
#reconstruction.FoDCS <- ace(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict), BrBo.Diet.DC.GS.SS.AP.trdata$phy, type = "d")

reconstruction.FoDCS <- as.vector(paste(BrBo.diet.trdata$dat$Fol.Non.Fol.Strict))
names(reconstruction.FoDCS)<-BrBo.diet.trdata$phy$tip.label
#reconstruction.FoDCS<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.FoDCS,model="ER",Q="empirical",nsim=sim.num)   
tree<-BrBo.diet.trdata$phy
x<-reconstruction.FoDCS

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.diet.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.diet.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.diet.trdata$phy,x,model="ARD")
saved.discrete.models<-rbind(saved.discrete.models,c("FoDCS",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))

test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]


fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states

trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.FoDCS<-trees

```

```{r}
########################
#Fol.Non.Fol.Per Diet Categories
#reconstruction.FoDC <- ace(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per), BrBo.Diet.DC.GS.SS.AP.trdata$phy, type = "d")

reconstruction.FoDC <- as.vector(paste(BrBo.diet.trdata$dat$Fol.Non.Fol.Per))
names(reconstruction.FoDC)<-BrBo.diet.trdata$phy$tip.label
#reconstruction.FoDC<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.FoDC,model="ER",Q="empirical",nsim=sim.num)   
tree<-BrBo.Diet.DC.GS.SS.AP.trdata$phy
x<-reconstruction.FoDC

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.diet.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.diet.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.diet.trdata$phy,x,model="ARD") #Slightly modified code

#num.cores=parallel::detectCores()-2

#system.time(
#fit.ARD<-fitMk(BrBo.Diet.DC.GS.SS.AP.trdata$phy,x,model="ARD",ncores=num.cores)) #Original Code

#system.time(
#fit.ARD<-fitMk(BrBo.Diet.DC.GS.SS.AP.trdata$phy,x,model="ARD"))

#cl = makeCluster(parallel::detectCores()-2) 
#system.time(
#fit.ARD<-fitMk(BrBo.Diet.DC.GS.SS.AP.trdata$phy,x,model="ARD")) #Slightly modified code

#system.time(
#fit.ARD<-fitMk(BrBo.Diet.DC.GS.SS.AP.trdata$phy,x,model="ARD")) #Slightly modified code

#system.time(
#fit.ARD<-fitMk(BrBo.Diet.DC.GS.SS.AP.trdata$phy,x,model="ARD"))

#setDefaultCluster(cl=NULL); stopCluster(cl) 


saved.discrete.models<-rbind(saved.discrete.models,c("FoDC",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))

test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]


fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states

trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.FoDC<-trees

```

```{r}
########################
#Frugivore Diet Categories
#reconstruction.FrDC <- ace(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ), BrBo.Diet.DC.GS.SS.AP.trdata$phy, type = "d")

reconstruction.FrDC <- as.vector(BrBo.diet.trdata$dat$Frug.Non.Frug.Per)
names(reconstruction.FrDC)<-BrBo.diet.trdata$phy$tip.label
#reconstruction.FrDC<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.FrDC,model="ER",Q="empirical",nsim=sim.num)   
tree<-BrBo.diet.trdata$phy
x<-reconstruction.FrDC

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.diet.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.diet.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.diet.trdata$phy,x,model="ARD")
saved.discrete.models<-rbind(saved.discrete.models,c("FrDC",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))
test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]

fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states
trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.FrDC<-trees

```

```{r}
########################
#Group Size Categories
#reconstruction.gsc <- ace(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size), BrBo.Diet.DC.GS.SS.AP.trdata$phy, type = "d")

reconstruction.gsc <- as.vector(BrBo.GS.trdata$dat$Cat.group.size)
names(reconstruction.gsc)<-BrBo.GS.trdata$phy$tip.label
#reconstruction.gsc<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.gsc,model="ER",Q="empirical",nsim=sim.num)  
tree<-BrBo.GS.trdata$phy
x<-reconstruction.gsc

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.GS.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.GS.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.GS.trdata$phy,x,model="ARD")
saved.discrete.models<-rbind(saved.discrete.models,c("GSC",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))
test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]

fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states
trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.gsc<-trees
 
```

```{r}
########################
#Social System
#reconstruction.ss <- ace(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass), BrBo.Diet.DC.GS.SS.AP.trdata$phy, type = "d")

reconstruction.ss <- as.vector(BrBo.SS.trdata$dat$Social.System.DRclass)
names(reconstruction.ss)<-BrBo.SS.trdata$phy$tip.label
#reconstruction.ss<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.ss,model="ER",Q="empirical",nsim=sim.num)   
tree<-BrBo.SS.trdata$phy
x<-reconstruction.ss

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.SS.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.SS.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.SS.trdata$phy,x,model="ARD")
saved.discrete.models<-rbind(saved.discrete.models,c("SS",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))
test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]

fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states
trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.ss<-trees



########################
#Mating System
#reconstruction.ms <- ace(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ Mating.System), BrBo.Diet.DC.GS.SS.AP.trdata$phy, type = "d")

reconstruction.ms <- as.vector(BrBo.SS.trdata$dat$ Mating.System)
names(reconstruction.ms)<-BrBo.SS.trdata$phy$tip.label
#reconstruction.ms<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.ms,model="ER",Q="empirical",nsim=sim.num)   
tree<-BrBo.SS.trdata$phy
x<-reconstruction.ms

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.SS.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.SS.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.SS.trdata$phy,x,model="ARD")
saved.discrete.models<-rbind(saved.discrete.models,c("Mating System",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))
test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]

fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states
trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.ms<-trees

```

```{r}
####Activity Pattern
reconstruction.ap <- as.vector(BrBo.GS.trdata$dat$Activity.Period.DN)
names(reconstruction.ap)<-BrBo.GS.trdata$phy$tip.label
#reconstruction.ms<-make.simmap(BrBo.Diet.DC.GS.SS.AP.trdata$phy,reconstruction.ms,model="ER",Q="empirical",nsim=sim.num)   
tree<-BrBo.GS.trdata$phy
x<-reconstruction.ap

## fit model so we don't have to repeatedly recompute Q
fit.ER<-fitMk(BrBo.GS.trdata$phy,x,model="ER")
fit.SYM<-fitMk(BrBo.GS.trdata$phy,x,model="SYM")
fit.ARD<-fitMk(BrBo.GS.trdata$phy,x,model="ARD")
saved.discrete.models<-rbind(saved.discrete.models,c("AP",AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD)))
test<-c(AIC(fit.ER),AIC(fit.SYM),AIC(fit.ARD))
num.min.AIC<-match(min(test),test)
fit<-list(fit.ER,fit.SYM,fit.ARD)[[num.min.AIC]]

fittedQ<-matrix(NA,length(fit$states),length(fit$states))
fittedQ[]<-c(0,fit$rates)[fit$index.matrix+1]
diag(fittedQ)<-0
diag(fittedQ)<--rowSums(fittedQ)
colnames(fittedQ)<-rownames(fittedQ)<-fit$states
trees<-mclapply(1:loops.num,function(n,tree,x,fixedQ) make.simmap(tree,x,Q=fixedQ,nsim=sim.num),
	tree=tree,x=x,fixedQ=fittedQ,mc.cores=num.cores)
trees<-do.call(c,trees) ## combine trees
if(!("multiSimmap"%in%class(trees))) class(trees)<-c("multiSimmap",class(trees))
reconstruction.ap<-trees


```

```{r}
saved.discrete.models<-saved.discrete.models[-1,]
```

```{r}
save.image("WS SIMMAP Only - Univariate 062822.RData")


```

```{r}
write.csv(saved.discrete.models,"SBR2_Saved_SIMMAP_modeltesting_062522.csv")

closeAllConnections()

```
