---
title: "R2 BDS ms SIMMAP Plots Code 091222"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

All Primates Analysis

Run: SIMMAPS 062522 v1
	Testing revised data from R2 but running original fitMk program, not parallel
	Gorilla g in strict classification is folivore
	Predictors:
		Fol.Non.Fol.Strict
		Fol.Non.Fol.Per
		Frug.Non.Frug.Per
		Social.System.DRclass
		Social.System.DGT
		Mating.System
		Activity.Period.DN
		GSC >50


```{r}
rm(list=ls())
library(ggplot2)
library(phytools)
library(ggsci)
library(bayou)
library(ggridges)
library(forcats)
library(dplyr)
#Get rid of return before making plots
devAskNewPage(ask = FALSE)

source("/Users/markgrabowski/Library/CloudStorage/GoogleDrive-mark.walter.grabowski@gmail.com/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/plotRegimesMod.R")

source("/Users/markgrabowski/Library/CloudStorage/GoogleDrive-mark.walter.grabowski@gmail.com/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.AICc.R2.dist.R")

```

Load All Primates Simmap WS
```{r}
#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/Scaled/WS from SIMMAP - All Primates - Scaled 042621.RData")

#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS from SIMMAP - All Primates - Scaled 051021.RData")

#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS from SIMMAP - Streps - Scaled 051321.RData")

#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS from SIMMAP - Haps - Scaled 051321.RData")

#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS from SIMMAP - Platys - Scaled 051321.RData")

###########################
#128 Species 
#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS from SIMMAP - All Primates - 128 sp - Scaled 051621.RData")


#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/128 sp/WS from SIMMAP - All Primates - 128 sp - Scaled 051621.RData")

#load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062122 v1/SIMMAPS/WS from SIMMAP - All Primates - Scaled 062122.RData")

#load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAPS/WS from SIMMAP - All Primates - Scaled 062522.RData")

load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAPS/All Primates/WS from SIMMAP - All Primates - Scaled 062522.RData")

```

Plot simmap: reconstruction.FoDC.ms -Folivore diet categories + Mating System
```{r}
#library(viridis)
#cols <- viridis(length(levels(as.factor(states))))

#############
states<-unique(as.vector(paste(BrBo.Diet.DC.GS.SS.trdata$dat$Fol.Non.Fol ,BrBo.Diet.DC.GS.SS.trdata$dat$Mating.System)))
cols<-pal_aaas(palette = c("default"),alpha=1.0)(length(states))
names(cols)<-levels(as.factor(states))

ltys<-rep(NA,length(levels(as.factor(states))))
names(ltys)<-levels(as.factor(states))
ltys[grepl("Non", names(ltys), fixed = TRUE)==TRUE]<-1
ltys[grepl("Non", names(ltys), fixed = TRUE)==FALSE]<-6

#Modified bayou plotRegime function - added in line type code
plotRegimesMod(reconstruction.FoDC.ms[[1]],col=cols, lwd = 1.75, lty = ltys,cex = 0.15)
#6X4 pdf
####


```

Make SIMMAP Pie Plot
```{r}
test.summary<-describe.simmap(reconstruction.FoDC.ms,plot=FALSE)

plot(test.summary,colors=cols,fsize=0.25,ftype="i",cex=0.6, lty=ltys)
add.simmap.legend(colors=cols,prompt=FALSE,x=0,y=40,vertical=TRUE,fsize=0.75)
#6X4

#Individual run
#plotSimmap(reconstruction.FoDC.ms[[1]],colors=cols,fsize=0.25,ftype="i")
#add.simmap.legend(colors=cols,prompt=FALSE,x=0,y=35,vertical=TRUE)



```

Plot simmap: reconstruction.FoDC.ms - Mating System
```{r}
#library(viridis)
#cols <- viridis(length(levels(as.factor(states))))

#############
states<-unique(as.vector(BrBo.Diet.DC.GS.SS.trdata$dat$Mating.System))
cols<-pal_aaas(palette = c("default"),alpha=1.0)(length(states))
names(cols)<-levels(as.factor(states))


ltys<-rep(NA,length(levels(as.factor(states))))
names(ltys)<-levels(as.factor(states))
ltys[]<-1

#Modified bayou plotRegime function - added in line type code
plotRegimesMod(reconstruction.ms[[2]],col=cols, lwd = 1.75, lty = ltys,cex = 0.15)
#6X4 pdf
####


```

Make SIMMAP Pie Plot
```{r}
test.summary<-describe.simmap(reconstruction.ms,plot=FALSE)

plot(test.summary,colors=cols,fsize=0.25,ftype="i",cex=0.6, lty=ltys)
add.simmap.legend(colors=cols,prompt=FALSE,x=0,y=40,vertical=TRUE,fsize=0.75)
#6X4

#Individual run
plotSimmap(reconstruction.FoDC.ms[[1]],colors=cols,fsize=0.25,ftype="i")
add.simmap.legend(colors=cols,prompt=FALSE,x=0,y=35,vertical=TRUE)



```




Summarize SIMMAP AICc distributions 
Setup
```{r}
test<-make.AICc.R2.dist(saved.slouch.output.list,loops.num*sim.num)

#Take out groupm size^2 rows
test<-test[!grepl("Group Size2", test$Predictor),]
test<-mutate(test,Model=NA)
test[grepl("OU.", test$`Model Type`),"Model"]<-"OU"
test[grepl(".BM", test$`Model Type`),"Model"]<-"BM"
test<-mutate(test,Merged=paste(Predictor,Model))
```



```{r}
ms.plot<-ggplot(test, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - All Primate Results")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=8),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=6),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
#16X12
```




```{r}
test.1st<-dim(test)[1]/2
test.first<-test[1:test.1st,]
test.second<-test[test.1st+1:dim(test)[1],]

```


```{r}
ms.plot<-ggplot(test.first, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - All Primate Results")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=8),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
#16X12

```


```{r}
ms.plot<-ggplot(test.second, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - All Primate Results")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=8),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
#16X12

```



Based on individual SIMMAP maps for groups, not subsets of all primates SIMMAP
############
Haplorrhines
```{r}
#128 Species 
load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAPS/Haplorhines/Version 2/WS from SIMMAP - Haplorrhines - Scaled 062722.RData")
```


Summarize SIMMAP AICc distributions 
Setup
```{r}
test<-make.AICc.R2.dist(saved.slouch.output.list,loops.num*sim.num)

#Take out groupm size^2 rows
test<-test[!grepl("Group Size2", test$Predictor),]
test<-mutate(test,Model=NA)
test[grepl("OU.", test$`Model Type`),"Model"]<-"OU"
test[grepl(".BM", test$`Model Type`),"Model"]<-"BM"
test<-mutate(test,Merged=paste(Predictor,Model))
```

SI Fig 1 and 2
```{r}
test.1st<-dim(test)[1]/2
test.first<-test[1:test.1st,]
test.second<-test[test.1st+1:dim(test)[1],]

```


```{r}
ms.plot<-ggplot(test.first, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - Haplorrhines")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
```


```{r}
ms.plot<-ggplot(test.second, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - Haplorrhines")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
```


############
Strepsirrhines
```{r}
load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAPS/Strepsirrhines/WS from SIMMAP - Strepsirrhines - Scaled 062722.RData")
```


Summarize SIMMAP AICc distributions 
Setup
```{r}
test<-make.AICc.R2.dist(saved.slouch.output.list,loops.num*sim.num)

#Take out groupm size^2 rows
test<-test[!grepl("Group Size2", test$Predictor),]
test<-mutate(test,Model=NA)
test[grepl("OU.", test$`Model Type`),"Model"]<-"OU"
test[grepl("BM", test$`Model Type`),"Model"]<-"BM"
test<-mutate(test,Merged=paste(Predictor,Model))
```





```{r}
test.1st<-dim(test)[1]/2
test.first<-test[1:test.1st,]
test.second<-test[test.1st+1:dim(test)[1],]

```


```{r}
ms.plot<-ggplot(test.first, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - Strepsirrhines")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=8),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
```


```{r}
ms.plot<-ggplot(test.second, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - Strepsirrhines")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=8),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
```


#######
Platyrrhines
```{r}
#128 Species 
load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAPS/Platyrrhines/Version 2/WS from SIMMAP - Platyrrhines - Scaled 062722.RData")
```
Summarize SIMMAP AICc distributions 
Setup
```{r}
test<-make.AICc.R2.dist(saved.slouch.output.list,loops.num*sim.num)

#Take out groupm size^2 rows
test<-test[!grepl("Group Size2", test$Predictor),]
test<-mutate(test,Model=NA)
test[grepl("OU.", test$`Model Type`),"Model"]<-"OU"
test[grepl("BM", test$`Model Type`),"Model"]<-"BM"
test<-mutate(test,Merged=paste(Predictor,Model))
```





```{r}
test.1st<-dim(test)[1]/2
test.first<-test[1:test.1st,]
test.second<-test[test.1st+1:dim(test)[1],]

```


```{r}
ms.plot<-ggplot(test.first, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - Platyrrhines")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
```


```{r}
ms.plot<-ggplot(test.second, aes(x = AICc, y = Merged)) + geom_density_ridges()+labs(title="SIMMAP - Platyrrhines")

ms.plot<-ms.plot+aes(y=fct_inorder(Merged))
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=8),legend.text=element_text(size=8),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16))
ms.plot<-ms.plot+scale_y_discrete(limits=rev)
ms.plot<-ms.plot+labs(y="Predictor/Model Type")

ms.plot
```




