---
title: "Bayou - Brain Size ~ Body Size"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
Setup for Bayou with Only BoM  - 03.04.2019 - after adding in new diet categories and correcting for using DC inferred evolution rather than RDC on RDC analysis
Also updated SS, and ran everything together under the Diet %, Reduced Diet Categories separators

Species Only Analysis
```{r}
#Clear workspace
closeAllConnections() 

#install.packages("devtools")
#require(devtools)
#install_github("uyedaj/bayou")
#require(bayou)

rm(list=ls())
library(ggplot2)
library(slouch)
library(phytools)
library(treeplyr)
#install.packages("bayou")
library(bayou)

library(doParallel)
library(treeplyr)

library(viridis)
library(patchwork)
library(gridGraphics)
library(tidyr)

options(scipen=999)

#For execution on a local, multicore CPU with excess RAM we recommend calling
options(mc.cores = parallel::detectCores())

#First, load workspace for all data:
#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/Bayou Brain Diet SS Rstudio Folder/Workspace/Full_Model_Setup_10K_101519.RData")
#127 species
#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS for bayou - SBR1 - 040821.RData")
#128 Species
#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/bayou/WS for bayou - SBR1 -128 sp 051721.RData")
```



```{r}
load("/Users/markgrabowski/Library/CloudStorage/GoogleDrive-mark.walter.grabowski@gmail.com/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/bayou/WS for bayou - SBR1 -128 sp 051721.RData")

```

```{r}
chain.BoM.N1.ch1<-readRDS("/Users/markgrabowski/Library/CloudStorage/GoogleDrive-mark.walter.grabowski@gmail.com/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Code/bayou Code/Output/modelBoM_N1_r001.chain.rds")
chain.BoM.N1.ch2<-readRDS("/Users/markgrabowski/Library/CloudStorage/GoogleDrive-mark.walter.grabowski@gmail.com/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Code/bayou Code/Output/modelBoM_N1_r002.chain.rds")
```

```{r}
chains.N1 <- combine.chains(list(chain.BoM.N1.ch1, chain.BoM.N1.ch2), burnin.prop=0.3)

```


Fig 1: Make Plots for Bayou
```{r}
library(ggsci)
#########################
par(mfrow=c(1,1))
par(bg = 'white')
#cols<-lib(4)

reg.colors<-pal_aaas(palette=c("default"),alpha=0.8)(9)
library(scales)
show_col(pal_aaas("default")(9))

#Posterior probabilities proportional to circle diameter:
pdf("Simmap_mcmc.pdf", height=6, width=4)

#No tip labels - main plot
plotSimmap.mcmc(chains.N1, cex=0.2,lwd=1.0,edge.type="regimes", pp.cutoff=0.5,circle.cex.max = 4.0,label.offset=1,pal = pal_aaas(),show.tip.label=FALSE)
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)

#With tip labels for SI
plotSimmap.mcmc(chains.N1, cex=0.2,lwd=1.0,edge.type="regimes", pp.cutoff=0.5,circle.cex.max = 4.0,label.offset=1,pal = pal_aaas(),show.tip.label=TRUE)
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)
 
#With edge labels
plotSimmap.mcmc(chains.N1, cex=0.2,lwd=1.0,edge.type="regimes",pp.cutoff=0.5,circle.cex.max = 1.0,circles=FALSE,pp.labels = TRUE,pp.cex=0.25)
edgelabels(cex=0.25,frame="none",adj=c(1,1))
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)

#Fig S1
plotBranchHeatMap(BrBo.DC.GS.SS.tree, chains.N1, variable="theta",pal=cm.colors,cex=0.2)




dev.off()


#4X6 -Fig 1, then cut out

```

Combine Theta info for intercept plot
```{r}
library(ggsci)
dat<-log.ECV.dat
pred<-log.BoM.dat
sumstats<-summary(chains.N1)
sumpars<-list(sb=which(sumstats$branch.posteriors$pp>0.5))
sumpars$k<-length(sumpars$sb)
sumpars$ntheta<-length(sumpars$sb)+1
sumpars$loc<-rep(0,sumpars$k)
sumpars$t2<-2:sumpars$ntheta
sb<-sumpars$sb
cache <- bayou:::.prepare.ou.univariate(BrBo.DC.GS.SS.tree,dat, SE=0, pred)
tipregs <- bayou:::.tipregime(sumpars, BrBo.DC.GS.SS.tree)
tr <- pars2simmap(sumpars, BrBo.DC.GS.SS.tree)
descendents <- lapply(1:(length(sumpars$sb)+1), function(x) names(tipregs[tipregs==x])) 

#betas<-do.call(rbind,chains.N1$beta_log.BoM.dat)
betas<-chains.N1$beta_log.BoM.dat
thetas<-do.call(rbind.data.frame,chains.N1$theta)
#thetas<-chains.N1$theta
thetas<-data.frame(thetas)


ids<-which(sapply(descendents,length)>3)
cladenames <- c("Root (28)", "Haplorhines (99)", "Callitrichidae (11)")
names(thetas)<-cladenames

thetas <- thetas[,ids]
ldesc <- sapply(ids, function(x) length(descendents[[x]]))
cols<-pal_aaas(palette=c("default"),alpha=0.8)(3)
#cols <- setNames(pal_aaas(length(sb)+1), c(1, sample(2:(length(sb)+1), length(sb), replace=FALSE)))
#cols <- cols[order(as.numeric(names(cols)))]

```

Bjorn's Code - working
```{r}
level_order <- c("Root (28)", "Haplorhines (99)", "Callitrichidae (11)")
#ggplot(iris, aes(x = factor(Species, level = level_order), y = Petal.Width)) + geom_col()

#remove 2.5/97.5 quantiles code
#quantiles <- c(0.025, 0.975)
#saved.quantiles<-apply(thetas,2,function(x){quantile(x,quantiles)})
#thetas[,1]


df_longformat <- 
  pivot_longer(thetas,
               col = everything(),
               names_to = "optima")

violin_plot <- df_longformat %>%
  ggplot(aes(x = factor(optima,level=level_order), y = value, fill = optima)) +
  geom_violin(draw_quantiles = c(0.975, 0.5, 0.025), alpha = 0.8,bw=0.25) +
  geom_boxplot(width=0.05,color="black",outlier.shape = NA)+
  stat_summary(fun=median, geom="point", shape=20, size=7, color="black", fill="black") +
  theme_classic() +
  ylab("Optimum\n(Endocranial volume, cc)") +
  theme(axis.title.x = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text=element_text(size=14),
        axis.title.y = element_text(size=14),
      

panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),
panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)

par(mar = c(0.1, 0.1, 0.1, 0.1), mgp = c(1, 0.25, 0), 
               bg = NA, cex.axis = 0.75, las = 1, tcl = -0.25)

meanx <- 8.09
slope <- 0.554 ## I dont know what hte slope is for this model, check it
scaleFUN <- function(x) sprintf("%.0f", round(exp(x + slope * meanx), 0))
breaks <- log(c(1,10, 100, 1000, 10000)) - slope * meanx

p2 <- violin_plot + 
  scale_y_continuous(labels = scaleFUN)+scale_fill_manual(values=cols[c(3,2,1)])

p2
```


```{r}
#####
require(vioplot)

par(mfrow=c(1,1), lwd=2)
par(mar=c(6, 5, 1, 1))
plot(0,0, type="n", xlab="", ylab="Intercept", xlim=c(0,4), ylim=c(-5,4.5), xaxt="n", cex.lab=1.25, yaxt="n")
abline(h=seq(-5,4.5,1), col="gray75",lty=3)

#axis(1, at=1:3, paste(cladenames, " (", ldesc,")", sep=""), las=2, cex=1.5)

axis(side=1, labels=FALSE)

text(x = 1:length(cladenames),
     y = par("usr")[3] - 0.45,
     labels = paste(cladenames, " (", ldesc,")", sep=""),
     xpd = NA,
     adj=1.1,
     ## Rotate the labels by 35 degrees.
     srt = 45,
     cex = 1)

axis(2, at=seq(-6,6,2), cex=1.25)
#abline(h=seq(-6,5,1), col="gray50")
lapply(1:length(ids), function(x) vioplot(thetas[,x], at=x, add=TRUE, col=cols[ids[x]], border="black"))
box()

#####
```


Combine Theta info for intercept plot
```{r}
library(ggsci)
dat<-log.ECV.dat
pred<-log.BoM.dat
sumstats<-summary(chains.N1)
sumpars<-list(sb=which(sumstats$branch.posteriors$pp>0.5))
sumpars$k<-length(sumpars$sb)
sumpars$ntheta<-length(sumpars$sb)+1
sumpars$loc<-rep(0,sumpars$k)
sumpars$t2<-2:sumpars$ntheta
sb<-sumpars$sb
cache <- bayou:::.prepare.ou.univariate(BrBo.DC.GS.SS.tree,dat, SE=0, pred)
tipregs <- bayou:::.tipregime(sumpars, BrBo.DC.GS.SS.tree)
tr <- pars2simmap(sumpars, BrBo.DC.GS.SS.tree)
descendents <- lapply(1:(length(sumpars$sb)+1), function(x) names(tipregs[tipregs==x])) 

#betas<-do.call(rbind,chains.N1$beta_log.BoM.dat)
betas<-chains.N1$beta_log.BoM.dat
thetas<-do.call(rbind.data.frame,chains.N1$theta)
#thetas<-chains.N1$theta
thetas<-data.frame(thetas)


ids<-which(sapply(descendents,length)>3)
cladenames <- c("Root", "Haplorhines", "Callitrichidae")
names(thetas)<-cladenames

thetas <- thetas[,ids]
ldesc <- sapply(ids, function(x) length(descendents[[x]]))
cols<-pal_aaas(palette=c("default"),alpha=0.8)(3)
#cols <- setNames(pal_aaas(length(sb)+1), c(1, sample(2:(length(sb)+1), length(sb), replace=FALSE)))
#cols <- cols[order(as.numeric(names(cols)))]

```




Rescaled to global mean body mass
Exponentated axis?
```{r}
root.theta<--1.278755650
call.theta<--1.8158816
haps.theta<-0.3655701
slope<-0.554489766
mean.ECV<-mean(log.ECV.dat)
mean.BoM<-mean(log.BoM.dat)

thetas.starred<-thetas
thetas.starred<-thetas+slope*8.085059
thetas.starred<-as.data.frame(thetas.starred)

#####
```

```{r}
require(vioplot)

par(mfrow=c(1,1), lwd=2)
par(mar=c(6, 5, 1, 1))
plot(0,0, type="n", xlab="", ylab="Optimum (Enocranial Volume in cc)", xlim=c(0,4), ylim=c(-1000,1000), xaxt="n", cex.lab=1.25, yaxt="n")
#abline(h=seq(-5,4.5,1), col="gray75",lty=3)

#axis(1, at=1:3, paste(cladenames, " (", ldesc,")", sep=""), las=2, cex=1.5)

axis(side=1, labels=FALSE)

text(x = 1:length(cladenames),
     y = par("usr")[3] - 0.45,
     labels = paste(cladenames, " (", ldesc,")", sep=""),
     xpd = NA,
     adj=1.1,
     ## Rotate the labels by 35 degrees.
     srt = 45,
     cex = 1)

axis(2, at=seq(-1000,1000,100), cex=1.25)
#abline(h=seq(-6,5,1), col="gray50")
lapply(1:length(ids), function(x) vioplot(round(exp(thetas.starred[,x])), at=x, add=TRUE, col=cols[ids[x]], border="black"))
box()

#####
```




```{r}
plotSimmap(tr$tree, colors=cols, ftype="off", mar=c(0.1,0.1,0.1,0.1))
require(vioplot)
plot(0,0, type="n", xlab="", ylab="Optima", xlim=c(0,4), ylim=c(-5,5), xaxt="n", cex.lab=1.25, yaxt="n")
abline(h=seq(-5,5,1), col="gray50",lty=2)
axis(1, at=1:3, paste(cladenames, " (", ldesc,")", sep=""), las=2, cex=1.5)
axis(side=1, labels=FALSE)
text(x = 1:length(cladenames),
     y = par("usr")[3] - 0.45,
     labels = names(paste(cladenames, " (", ldesc,")", sep="")),
     xpd = NA,
     ## Rotate the labels by 35 degrees.
     srt = 45,
     cex = 1.25)
text(seq(1, 3, by=1), par("usr")[3] - 0.2, labels = lablist, srt = 45, pos = 1, xpd = TRUE)
axis(2,  cex=1.25)
#abline(h=c(2/3, 0.75), lty=2, lwd=3)
lapply(1:length(ids), function(x) vioplot(thetas[,x], at=x, add=TRUE, col=cols[ids[x]], cex=2))
box()


```

GGplot
```{r}
library(ggsci)
library(ggplot2)
library(reshape2)
sumstats<-summary(chains.N1)
sumpars<-list(sb=which(sumstats$branch.posteriors$pp>0.5))
sumpars$k<-length(sumpars$sb)
sumpars$ntheta<-length(sumpars$sb)+1
sumpars$loc<-rep(0,sumpars$k)
sumpars$t2<-2:sumpars$ntheta
sb<-sumpars$sb
tipregs <- bayou:::.tipregime(sumpars, BrBo.DC.GS.SS.tree)
tr <- pars2simmap(sumpars, BrBo.DC.GS.SS.tree)
descendents <- lapply(1:(length(sumpars$sb)+1), function(x) names(tipregs[tipregs==x])) 

thetas<-do.call(rbind,chains.N1$theta)
thetas<-data.frame(thetas)
ids<-which(sapply(descendents,length)>3)
cladenames <- c("Root", "Haplorhines", "Callitrichidae")
names(thetas)<-cladenames

thetas <- thetas[,ids]
ldesc <- sapply(ids, function(x) length(descendents[[x]]))
ldesc<-ldesc[c(1,3,2)]
cols<-pal_aaas(palette=c("default"),alpha=0.8)(3)

thetas<-melt(thetas)
head(thetas)

```

```{r}

addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

##############
v.plot<-ggplot(thetas.starred,aes(x=variable,y=round(exp(value)),fill=variable))+geom_violin()
#v.plot<- v.plot + stat_summary(fun=median, geom="point", size=2, color="black")
v.plot<-v.plot+ geom_boxplot(width=0.05,color="black",outlier.shape = NA)
#v.plot<-v.plot+ geom_pointrange(mapping = aes(x = variable, y = value), stat = "summary" ,fun.y = "median",geom="point")
v.plot<-v.plot+stat_summary(fun.y="median",geom="point")
v.plot<-v.plot+scale_fill_manual(values=cols)
v.plot<-v.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=14),axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=12),

# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),
panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16),
,legend.position="none"
)
v.plot<-v.plot+scale_x_discrete(name ="Clade",labels=addline_format(c(paste(cladenames, " (", ldesc,")", sep=""))))
v.plot<-v.plot + labs(y="Optima (Endocranial Volume - g)")
v.plot



```

