---
title: "SB R2 BDS ms Intercept Plots - Strepsirrhines"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
Strepsirrhines Analysis

Run: SIMMAPS 062522 v1
	Testing revised data from R2 but running original fitMk program, not parallel
	Gorilla g in strict classification is folivore
	Predictors:
		Fol.Non.Fol.Strict
		Fol.Non.Fol.Per
		Frug.Non.Frug.Per
		Social.System.DRclass
		Social.System.DGT
		Mating.System
		GSC >50
		Activity Period
		
Setup
```{r}
rm(list=ls())
library(ggplot2)
library(phytools)
library(viridis)
library(RColorBrewer)
library("ggsci")
library(directlabels)
library(dplyr)
library(plyr)


load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAP ACE/Strepsirrhines/SBR2 - WS from SIMMAP ACE - Strepsirrhines - Scaled 062522.RData")
```


#######
Fig. S7b: MS + AP Reconstructions Phylogeny
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),factor(internal.regimes.ms.ap[1:27]))

levels(regimes)

regimes <- factor(regimes, levels = c("Spatial Polygyny Nocturnal","Monogamy Nocturnal","Monogamy Diurnal","Polygynandry Diurnal"))

edge_regimes <- factor(regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])

reg.colors<-pal_aaas()(length(unique(regimes)))

show_col(reg.colors)

###################

plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge_regimes],edge.width = 1.75, cex = 0.5)
#6X5
```


Fig. S10a: Diet Categories + MS Reconstructions Regression Plot
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)))

regimes <- factor(regimes, levels = c("Spatial Polygyny Nocturnal","Monogamy Nocturnal","Monogamy Diurnal","Polygynandry Diurnal"))


#############
test<-ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients
#rownames(test)<-gsub("Fol","Folivorous",rownames(test))
#rownames(test)<-gsub("Non","Non-folivorous",rownames(test))


intercepts<-test[match(levels(regimes),rownames(test)),]
intercepts
#reg.colors<-pal_aaas()(length(unique(reordered.regimes)))
slope<-ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients[5]

```


```{r}
ms.plot<-ggplot(BrBo.Diet.DC.GS.SS.AP.trdata$dat,aes(y=log(ECV.species.mean),x=log(Body.mass.species.mean),fill=regimes))

ms.plot<-ms.plot+geom_point(size=3.5,color="white",pch=21) 
ms.plot<-ms.plot+xlab("log Body Mass (g)")+ylab("log Endocranial Volume (cc)")
                                     ms.plot<-ms.plot+theme(axis.text=element_text(size=16),axis.title=element_text(size=16),legend.title=element_text(size=10),legend.text=element_text(size=12),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),
panel.border = element_rect(colour = "black", fill=NA, size=0.5)
#,legend.position="none"
)
ms.plot<-ms.plot+theme(legend.key = element_rect(fill = "white"),legend.title = element_text(size=14))
#+scale_x_continuous(expand=c(0.5,0))


ms.plot<-ms.plot+geom_abline(intercept = intercepts[1,1],slope=slope,color=reg.colors[1],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[2,1],slope=slope,color=reg.colors[2],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[3,1],slope=slope,color=reg.colors[3],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[4,1],slope=slope,color=reg.colors[4],linetype=1,size=0.75)

ms.plot<-ms.plot+
scale_fill_manual(values=reg.colors,name="Mating System + \nActivity Period",labels=row.names(intercepts))

#ms.plot<-ms.plot+guides(fill = guide_legend(override.aes = list(size=5)))
ms.plot

#6 X 9 Small Pdf
#8 X 12, large PDF
#library(plotly)
#ggplotly()
```

Intercept Plots
```{r}
detach("package:plyr", unload=TRUE)

library(dplyr)

regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)))

regimes <- factor(regimes, levels = c("Spatial Polygyny Nocturnal","Monogamy Nocturnal","Monogamy Diurnal","Polygynandry Diurnal"))


log.BoM.grand.mean<-mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean))

BoM.category.data<-data.frame(BrBo.Diet.DC.GS.SS.AP.trdata$dat,Categories=as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)))

BoM.category.data<-data.frame(BoM.category.data,Genus_Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label)

#BoM.category.data$Categories<-gsub("Non-folivorous","Non",BoM.category.data$Categories)
#BoM.category.data$Categories<-gsub("Folivorous","Fol",BoM.category.data$Categories)

BoM.category.data
#################################

BoM.category.means<-data.frame(BoM.category.data%>%group_by(Categories)%>%summarize(log.ECV.mean=mean(log(ECV.species.mean),na.rm=TRUE),log.BoM.mean=mean(log(Body.mass.species.mean),na.rm=TRUE)))

#BoM.category.means<-cbind(BoM.category.means,intercepts[match(row.names(intercepts),BoM.category.means$Categories),])

BoM.category.means<-cbind(BoM.category.means,intercepts[match(BoM.category.means$Categories,row.names(intercepts)),])


BoM.category.means<-data.frame(BoM.category.means%>%group_by(Categories)%>%mutate(pred.ECV=slope*log.BoM.grand.mean+Estimates))
#BoM.category.means<-data.frame(BoM.category.means%>%group_by(Categories)%>%mutate(pred.ECV=slope*log.BoM.mean+Intercept))

#Reorder means
BoM.category.means<-BoM.category.means[match(levels(regimes),BoM.category.means$Categories),]

#Turn your 'treatment' column into a character vector
BoM.category.means$Categories <- as.character(BoM.category.means$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.means$Categories <- factor(BoM.category.means$Categories, levels=unique(BoM.category.means$Categories))

BoM.category.means
###################

BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(log.ECV.mean=mean(log(ECV.species.mean),na.rm=TRUE),log.BoM.mean=mean(log(Body.mass.species.mean),na.rm=TRUE)))

BoM.category.data$Estimates<-BoM.category.means$Estimates[match(BoM.category.data$Categories,BoM.category.means$Categories)]

#BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(y.delta=log(ECV.species.mean)-(slope*log(Body.mass.species.mean)+Intercept),y.new=slope*log.BoM.mean+Intercept+y.delta))

BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(y.delta=log(ECV.species.mean)-(slope*log(Body.mass.species.mean)+Estimates),y.new=slope*log.BoM.grand.mean+Estimates+y.delta))

#Reorder Rows to match categories  
BoM.category.data<-BoM.category.data%>%arrange(factor(Categories,levels=levels(regimes)))

#Turn your 'treatment' column into a character vector
BoM.category.data$Categories <- as.character(BoM.category.data$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.data$Categories <- factor(BoM.category.data$Categories, levels=unique(BoM.category.data$Categories))


####
#reordered.regimes.non.fol <-c("Spatial Polygyny Nocturnal","Spatial Polygyny Diurnal","Monogamy Nocturnal","Monogamy Diurnal","Polyandry Diurnal","Polygynandry Nocturnal","Polygynandry Diurnal","Harem Polygyny Diurnal")

#reg.colors<-pal_aaas()(length(unique(reordered.regimes.non.fol)))

library(scales)
show_col(reg.colors)

#gsc.ap.regimes<-c(1,3,6,8,9,1,2,3,4,5,6,7,8,9,10)
#error.bar.type<-c(4,4,4,1,1,1,1,1)

labels<-c("SPN","MN","MD","PGD")

#reordered.single.regimes<-c("Folivorous Spatial Polygyny Nocturnal","Folivorous Monogamy Nocturnal","Folivorous Monogamy Diurnal","Folivorous Polygynandry Diurnal","Folivorous Harem Polygyny Diurnal","Non-folivorous Spatial Polygyny Nocturnal","Non-folivorous Spatial Polygyny Diurnal","Non-folivorous Monogamy Nocturnal","Non-folivorous Monogamy Diurnal","Non-folivorous Polyandry Diurnal","Non-folivorous Polygynandry Nocturnal","Non-folivorous Polygynandry Diurnal", "Non-folivorous Harem Polygyny Diurnal")


#################
ms.plot<-ggplot(data=BoM.category.means,aes(x=Categories,y=pred.ECV))+
  geom_jitter(BoM.category.data,mapping=aes(x=Categories,y=y.new,fill=Categories),size=2.5,color="white",alpha=0.5,width=0.1,pch=21)+
  #geom_errorbar(aes(ymin=pred.ECV-Std..error,ymax=pred.ECV+Std..error),width=0.2,linetype=error.bar.type)+
  geom_errorbar(aes(ymin=pred.ECV-Std..error,ymax=pred.ECV+Std..error),width=0.2,linetype=1)+
  geom_point(data=BoM.category.means,mapping=aes(fill=Categories),size=5,color="white",pch=21)+ggtitle("Strepsirrhines")
  
ms.plot<-ms.plot+xlab("Mating System + Activity Period")+ylab("ECV (cc)")

#Add extant species to plot
#ms.plot<-ms.plot+geom_point(BoM.category.data,mapping=aes(x=Categories,y=log(ECV.species.mean),fill=Categories),pch=21,size=2,color="white",position="jitter",alpha=0.5)

                                          
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=10),legend.text=element_text(size=12),
axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=10),
#plot.margin=unit(c(5.5,5.5,5.5,40),"points"),

#In the case it's helpful to anyone else, here are the arguments to margin (denoting to which side each value corresponds): margin(t = 0, r = 0, b = 0, l = 0, unit = "pt") – Joshua Rosenberg Mar 20 '18 at 0:14


# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)
ms.plot<-ms.plot+

scale_fill_manual(values=reg.colors,name="Mating System\n + Activity Period",labels=row.names(intercepts))


#ms.plot<-ms.plot+scale_fill_manual(values=reg.colors)
ms.plot<-ms.plot+theme(legend.position = "none")
ms.plot<-ms.plot+scale_x_discrete(labels=c(labels))
#ms.plot<-ms.plot+theme(legend.key = element_rect(fill = "white"),legend.title = element_text(size=14) )
ms.plot

#5X5
```

####################

Fig. 9b: Diet Phylogeny
```{r}
reg.colors<-pal_aaas()(length(unique(as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict))))

regimes<-c(as.character(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict),as.character(internal.regimes.FoDCS))
fol.regimes<-gsub("Non.Fol","1",regimes)
fol.regimes<-gsub("Fol","6",fol.regimes)
edge.regimes <- factor(regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])
fol.edge.regimes <- as.numeric(fol.regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])

plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge.regimes], edge.lty = fol.edge.regimes,edge.width = 1.75, cex = 0.5)

#6X5

```



Fig. 9a: Diet Categories Regression Plot
```{r}
regimes<-BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict

#############
test<-ECV.FoDCS.BoM.BM$beta_primary$coefficients
rownames(test)<-gsub("Fol","Folivorous",rownames(test))
rownames(test)<-gsub("Non.F","Non-f",rownames(test))


regimes<-gsub("Fol","Folivorous",regimes)
regimes<-gsub("Non.F","Non-f",regimes)
regimes<-as.factor(regimes)

intercepts<-test[match(levels(regimes),rownames(test)),]
intercepts
#reg.colors<-pal_aaas()(length(unique(reordered.regimes)))
slope<-ECV.FoDCS.BoM.BM$beta_primary$coefficients[3]

```


```{r}
ms.plot<-ggplot(BrBo.Diet.DC.GS.SS.AP.trdata$dat,aes(y=log(ECV.species.mean),x=log(Body.mass.species.mean),fill=regimes,shape=regimes))

ms.plot<-ms.plot+geom_point(size=3.5,color="white") 
ms.plot<-ms.plot+xlab("log Body Mass (g)")+ylab("log Endocranial Volume (cc)")
                                     ms.plot<-ms.plot+theme(axis.text=element_text(size=16),axis.title=element_text(size=16),legend.title=element_text(size=10),legend.text=element_text(size=12),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),
panel.border = element_rect(colour = "black", fill=NA, size=0.5)
#,legend.position="none"
)
ms.plot<-ms.plot+theme(legend.key = element_rect(fill = "white"),legend.title = element_text(size=14))
#+scale_x_continuous(expand=c(0.5,0))


ms.plot<-ms.plot+geom_abline(intercept = intercepts[1,1],slope=slope,color=reg.colors[1],linetype=2,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[2,1],slope=slope,color=reg.colors[2],linetype=1,size=0.75)

ms.plot<-ms.plot+
scale_fill_manual(values=reg.colors,name="Diet",labels=row.names(intercepts))+
scale_shape_manual(values=c(22,21),name="Diet",labels=row.names(intercepts))

#ms.plot<-ms.plot+guides(fill = guide_legend(override.aes = list(size=5)))
ms.plot

#6 X 8 Small Pdf
#library(plotly)
#ggplotly()
```

Diet Intercept Plots
```{r}
detach("package:plyr", unload=TRUE)

library(dplyr)


regimes<-BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict
regimes<-gsub("Non.Fol","Non-folivorous",regimes)
regimes<-as.factor(gsub("Fol","Folivorous",regimes))


log.BoM.grand.mean<-mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean))

BoM.category.data<-data.frame(BrBo.Diet.DC.GS.SS.AP.trdata$dat,Categories=as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict))

BoM.category.data<-data.frame(BoM.category.data,Genus_Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label)

BoM.category.data$Categories<-gsub("Non.Fol","Non-folivorous",BoM.category.data$Categories)
BoM.category.data$Categories<-gsub("Fol","Folivorous",BoM.category.data$Categories)

BoM.category.data
#################################

BoM.category.means<-data.frame(BoM.category.data%>%group_by(Categories)%>%summarize(log.ECV.mean=mean(log(ECV.species.mean),na.rm=TRUE),log.BoM.mean=mean(log(Body.mass.species.mean),na.rm=TRUE)))

#BoM.category.means<-cbind(BoM.category.means,intercepts[match(row.names(intercepts),BoM.category.means$Categories),])

BoM.category.means<-cbind(BoM.category.means,intercepts[match(BoM.category.means$Categories,row.names(intercepts)),])


BoM.category.means<-data.frame(BoM.category.means%>%group_by(Categories)%>%mutate(pred.ECV=slope*log.BoM.grand.mean+Estimates))
#BoM.category.means<-data.frame(BoM.category.means%>%group_by(Categories)%>%mutate(pred.ECV=slope*log.BoM.mean+Intercept))

#Reorder means
BoM.category.means<-BoM.category.means[match(levels(regimes),BoM.category.means$Categories),]

#Turn your 'treatment' column into a character vector
BoM.category.means$Categories <- as.character(BoM.category.means$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.means$Categories <- factor(BoM.category.means$Categories, levels=unique(BoM.category.means$Categories))

BoM.category.means
###################

BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(log.ECV.mean=mean(log(ECV.species.mean),na.rm=TRUE),log.BoM.mean=mean(log(Body.mass.species.mean),na.rm=TRUE)))

BoM.category.data$Estimates<-BoM.category.means$Estimates[match(BoM.category.data$Categories,BoM.category.means$Categories)]

#BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(y.delta=log(ECV.species.mean)-(slope*log(Body.mass.species.mean)+Intercept),y.new=slope*log.BoM.mean+Intercept+y.delta))

BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(y.delta=log(ECV.species.mean)-(slope*log(Body.mass.species.mean)+Estimates),y.new=slope*log.BoM.grand.mean+Estimates+y.delta))

#Reorder Rows to match categories  
BoM.category.data<-BoM.category.data%>%arrange(factor(Categories,levels=levels(regimes)))

#Turn your 'treatment' column into a character vector
BoM.category.data$Categories <- as.character(BoM.category.data$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.data$Categories <- factor(BoM.category.data$Categories, levels=unique(BoM.category.data$Categories))


####
#reordered.regimes.non.fol <-c("Spatial Polygyny Nocturnal","Spatial Polygyny Diurnal","Monogamy Nocturnal","Monogamy Diurnal","Polyandry Diurnal","Polygynandry Nocturnal","Polygynandry Diurnal","Harem Polygyny Diurnal")

#reg.colors<-pal_aaas()(length(unique(reordered.regimes.non.fol)))

library(scales)
show_col(reg.colors)


labels<-c("Folivorous","Non-folivorous")

#reordered.single.regimes<-c("Folivorous Spatial Polygyny Nocturnal","Folivorous Monogamy Nocturnal","Folivorous Monogamy Diurnal","Folivorous Polygynandry Diurnal","Folivorous Harem Polygyny Diurnal","Non-folivorous Spatial Polygyny Nocturnal","Non-folivorous Spatial Polygyny Diurnal","Non-folivorous Monogamy Nocturnal","Non-folivorous Monogamy Diurnal","Non-folivorous Polyandry Diurnal","Non-folivorous Polygynandry Nocturnal","Non-folivorous Polygynandry Diurnal", "Non-folivorous Harem Polygyny Diurnal")


#################
ms.plot<-ggplot(data=BoM.category.means,aes(x=Categories,y=pred.ECV))+
  geom_jitter(BoM.category.data,mapping=aes(x=Categories,y=y.new,fill=Categories,shape=Categories),size=2.5,color="white",alpha=0.5,width=0.1)+
  #geom_errorbar(aes(ymin=pred.ECV-Std..error,ymax=pred.ECV+Std..error),width=0.2,linetype=error.bar.type)+
  geom_errorbar(aes(ymin=pred.ECV-Std..error,ymax=pred.ECV+Std..error),width=0.2,linetype=1)+
  geom_point(data=BoM.category.means,mapping=aes(fill=Categories),size=5,color="white",pch=21)+ggtitle("Strepsirrhines")
  
ms.plot<-ms.plot+xlab("Diet")+ylab("ECV (cc)")

#Add extant species to plot
#ms.plot<-ms.plot+geom_point(BoM.category.data,mapping=aes(x=Categories,y=log(ECV.species.mean),fill=Categories),pch=21,size=2,color="white",position="jitter",alpha=0.5)

                                          
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=10),legend.text=element_text(size=12),
axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=10),
#plot.margin=unit(c(5.5,5.5,5.5,40),"points"),

#In the case it's helpful to anyone else, here are the arguments to margin (denoting to which side each value corresponds): margin(t = 0, r = 0, b = 0, l = 0, unit = "pt") – Joshua Rosenberg Mar 20 '18 at 0:14


# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)
ms.plot<-ms.plot+

scale_fill_manual(values=reg.colors,name="Diet",labels=row.names(intercepts))+
scale_shape_manual(values=c(22,21),name="Diet",labels=row.names(intercepts))



#ms.plot<-ms.plot+scale_fill_manual(values=reg.colors)
ms.plot<-ms.plot+theme(legend.position = "none")
ms.plot<-ms.plot+scale_x_discrete(labels=c(labels))
#ms.plot<-ms.plot+theme(legend.key = element_rect(fill = "white"),legend.title = element_text(size=14) )
ms.plot

#5X5
```

