---
title: "SBR2 - Fig 2 Plots - mean centered data"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
Run: Using SIMMAPS 062522 v1 data originally
Mean centered brain and body size, then ran the best model for each group in Slouch


```{r}
rm(list=ls())
library(ggplot2)
library(phytools)
library(viridis)
library(RColorBrewer)
library("ggsci")
library(directlabels)
library(dplyr)
library(plyr)
library(scales)

#Load workspace
load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/Runs for Fig 2 091522/All Primates/SBR2 - WS from All Primates - Fig 2.RData")
```



################
Using residuals from model for ECV

##############################################
## All Primates

```{r}
detach("package:plyr", unload=TRUE)

library(dplyr)

single.regimes<-c("Fol Spatial Polygyny","Fol Monogamy","Fol Polygynandry","Fol Harem Polygyny","Non Spatial Polygyny","Non Monogamy","Non Polyandry","Non Polygynandry", "Non Harem Polygyny")

log.BoM.grand.mean<-mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean))

trends<-ECV.FoDCS.GS.MS.BoM.BM$beta_primary$coefficients_bias_corr[1:9,1]
slope<-ECV.FoDCS.GS.MS.BoM.BM$beta_primary$coefficients_bias_corr[10,]
trends<-cbind("Trends"=trends,SE=ECV.FoDCS.GS.MS.BoM.BM$beta_primary$coefficients_bias_corr[1:9,2])
rownames(trends)<-gsub("Non.Fol","Non",rownames(trends))
trends<-data.frame(trends)
trends$Categories<-rownames(trends)
residuals<-data.frame(Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,residuals=ECV.BoM.BM$beta_primary$residuals_bias_corr)

trends<-data.frame(trends%>%group_by(Categories)%>%mutate(pred.ECV=slope[1]*log.BoM.grand.mean+Trends))


```

```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),factor(internal.regimes.FoDCS.ms))

#regimes<-internal.regimes.FoDC.ms.ap

#regimes <- factor(regimes, levels = c("Folivorous Spatial Polygyny Nocturnal","Folivorous Monogamy Nocturnal","Folivorous Monogamy Diurnal","Folivorous Polygynandry Diurnal","Folivorous Harem Polygyny Diurnal","Non-folivorous Spatial Polygyny Nocturnal","Non-folivorous Spatial Polygyny Diurnal","Non-folivorous Monogamy Nocturnal","Non-folivorous Monogamy Diurnal","Non-folivorous Polyandry Diurnal","Non-folivorous Polygynandry Diurnal", "Non-folivorous Harem Polygyny Diurnal"))

regimes<-gsub("Non.Fol","Non",regimes)
sub.regimes<-substring(regimes,5)

fol.regimes<-substring(regimes,1,3)

sub.regimes <- factor(sub.regimes, levels = c("Spatial Polygyny","Monogamy","Polyandry","Polygynandry","Harem Polygyny"))

levels(sub.regimes)

reg.colors<-pal_aaas()(length(unique(sub.regimes)))

fol.shapes<-c(21,22)

```

Setup for Scaling Data to grand mean
```{r}
BoM.category.data<-data.frame(BrBo.Diet.DC.GS.SS.AP.trdata$dat,Categories=as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)))

BoM.category.data<-data.frame(BoM.category.data,Genus_Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label)

BoM.category.data$Categories<-gsub("Non.Fol","Non",BoM.category.data$Categories)
BoM.category.data$Categories<-gsub("Folivorous","Fol",BoM.category.data$Categories)

BoM.category.data
#################################
```

Scaling Species Data
```{r}
#BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(log.ECV.mean=mean(log(ECV.species.mean),na.rm=TRUE),log.BoM.mean=mean(log(Body.mass.species.mean),na.rm=TRUE)))

BoM.category.data$Residuals<-residuals$residuals[match(BoM.category.data$Genus_Species,residuals$Species)]

BoM.category.data$Trends<-trends$Trends[match(BoM.category.data$Categories,trends$Categories)]

#BoM.category.data<-data.frame(BoM.category.data%>%group_by(Categories)%>%mutate(y.delta=log(ECV.species.mean)-(slope[1]*log(Body.mass.species.mean)+Trends),y.new=slope[1]*log.BoM.grand.mean+Trends+y.delta))

#BoM.category.data<-data.frame(BoM.category.data%>%mutate(y.delta=log(ECV.species.mean)-(slope[1]*log(Body.mass.species.mean)+Trends),y.new=slope[1]*log.BoM.grand.mean+Trends+y.delta))




```


```{r}
#Reorder Rows to match categories  
#BoM.category.data<-BoM.category.data%>%arrange(factor(Categories,levels=single.regimes))
#Turn your 'treatment' column into a character vector
BoM.category.data$Categories <- as.character(BoM.category.data$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.data$Categories <- factor(BoM.category.data$Categories, levels=single.regimes)

#Turn your 'treatment' column into a character vector
trends$Categories <- as.character(trends$Categories)
#Then turn it back into a factor with the levels in the correct order
trends$Categories <- factor(trends$Categories, levels=single.regimes)


```


Plot on Log Scale - using residuals
```{r}
meanLogBrainECV <- mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean))
scaleFUN <- function(x){sprintf("%.0f", round(exp(x + meanLogBrainECV), 1))}


library(scales)
show_col(reg.colors)

#gsc.ap.regimes<-c(1,3,6,8,9,1,2,3,4,5,6,7,8,9,10)
error.bar.type<-c(4,4,4,4,1,1,1,1,1)

labels<-c("FSP","FM","FPG","FHP","NFSP","NFM","NFP","NFPG","NFHP")

#################
ms.plot<-ggplot(data=trends,aes(x=Categories,y=Trends))+
  geom_jitter(BoM.category.data,mapping=aes(x=Categories,y=Residuals,fill=Categories,shape=Categories),size=2.5,color="white",alpha=0.5,width=0.1)+
  geom_errorbar(aes(ymin=Trends-SE,ymax=Trends+SE),width=0.2,linetype=1)+
  geom_point(data=trends,mapping=aes(fill=Categories,shape=Categories),size=5,color="white")+ggtitle("All Primates")
  
ms.plot<-ms.plot+xlab("Diet + Mating System")+ylab("Endocranial Volume (cc)")

#Add extant species to plot
#ms.plot<-ms.plot+geom_point(BoM.category.data,mapping=aes(x=Categories,y=log(ECV.species.mean),fill=Categories),pch=21,size=2,color="white",position="jitter",alpha=0.5)

                                          
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=10),legend.text=element_text(size=12),
axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=10),
#plot.margin=unit(c(5.5,5.5,5.5,40),"points"),

#In the case it's helpful to anyone else, here are the arguments to margin (denoting to which side each value corresponds): margin(t = 0, r = 0, b = 0, l = 0, unit = "pt") – Joshua Rosenberg Mar 20 '18 at 0:14


# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)
ms.plot<-ms.plot+

scale_fill_manual(values=reg.colors[c(1,2,4,5,1,2,3,4,5)],name="Diet + Mating System",labels=single.regimes)+
scale_shape_manual(values=fol.shapes[c(2,2,2,2,1,1,1,1,1)],name="Diet + Mating System",labels=single.regimes)


#ms.plot<-ms.plot+scale_fill_manual(values=reg.colors)
ms.plot<-ms.plot+theme(legend.position = "none")
ms.plot<-ms.plot+scale_x_discrete(labels=c(labels))
ms.plot <- ms.plot + scale_y_continuous(labels = scaleFUN)

ms.plot

#5X5
```




######################
##Haplorhines
```{r}
rm(list=ls())

#Load workspace

load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/Runs for Fig 2 091522/Haplorhines/SBR2 - WS from Haplorhines - Fig 2.RData")
```

Fig. S10b: Diet Categories + MS Reconstructions Phylogeny
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),factor(internal.regimes.FoDCS.ms))

regimes<-gsub("Non.Fol","Non",regimes)
sub.regimes<-substring(regimes,5)

fol.regimes<-substring(regimes,1,3)

sub.regimes <- factor(sub.regimes, levels = c("Spatial Polygyny","Monogamy","Polyandry","Polygynandry","Harem Polygyny"))

levels(sub.regimes)

reg.colors<-pal_aaas()(length(unique(sub.regimes)))

show_col(reg.colors)


###################

edge.regimes <- factor(sub.regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])
fol.edge.regimes <- as.numeric(factor(fol.regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]]))


#edge.regimes <-factor(sub.regimes)
#fol.edge.regimes <- as.numeric(factor(fol.regimes))
#BrBo.Diet.DC.GS.SS.AP.trdata

#plot(BrBo.Diet.DC.GS.SS.trdata$phy,edge.color = reg.colors[edge.regimes], edge.width = 1.75, cex = 0.3) #10X12
fol.edge.regimes[fol.edge.regimes==1]<-6
fol.edge.regimes[fol.edge.regimes==2]<-1
#fol.edge.regimes[fol.edge.regimes==3]<-2
#fol.non.categories[fol.non.categories$BrBo.Diet.DC.GS.SS.trdata.dat.Fol.Non.Fol=="Non",1]<-1
#fol.non.categories[fol.non.categories$BrBo.Diet.DC.GS.SS.trdata.dat.Fol.Non.Fol!="Non",1]<-2
plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge.regimes], edge.lty = fol.edge.regimes,edge.width = 1.75, cex = 0.000001)
#6X4
```


Fig. S10a: Diet Categories + MS Reconstructions Regression Plot
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)))
levels(regimes)

regimes<-gsub("Non.Fol","Non",regimes)

regimes <- factor(regimes, levels = c("Fol Polygynandry","Fol Harem Polygyny","Non Spatial Polygyny","Non Monogamy","Non Polyandry","Non Polygynandry", "Non Harem Polygyny"))

sub.regimes<-substring(regimes,5)

fol.regimes<-substring(regimes,1,3)
fol.regimes <- factor(fol.regimes, levels = c("Non","Fol"))
fol.shapes<-c(21,22)

sub.regimes <- factor(sub.regimes, levels = c("Spatial Polygyny","Monogamy","Polyandry","Polygynandry","Harem Polygyny"))

levels(sub.regimes)

reg.colors<-pal_aaas()(length(unique(sub.regimes)))

show_col(reg.colors)

#############
test<-ECV.FoDCS.MS.BoM.BM$beta_primary$coefficients
#rownames(test)<-gsub("Fol","Folivorous",rownames(test))
rownames(test)<-gsub("Non.Fol","Non",rownames(test))

#rownames(test)<-gsub("Folivorous","Fol",rownames(test))


intercepts<-test[match(levels(regimes),rownames(test)),]
intercepts
#reg.colors<-pal_aaas()(length(unique(reordered.regimes)))
slope<-ECV.FoDCS.MS.BoM.BM$beta_primary$coefficients[8]



```


```{r}
detach("package:plyr", unload=TRUE)

library(dplyr)

single.regimes<-c("Fol Polygynandry","Fol Harem Polygyny","Non Spatial Polygyny","Non Monogamy","Non Polyandry","Non Polygynandry", "Non Harem Polygyny")

log.BoM.grand.mean<-mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean))

trends<-ECV.FoDCS.MS.BoM.BM$beta_primary$coefficients_bias_corr[1:7,1]
slope<-ECV.FoDCS.MS.BoM.BM$beta_primary$coefficients_bias_corr[8,]
trends<-cbind("Trends"=trends,SE=ECV.FoDCS.MS.BoM.BM$beta_primary$coefficients_bias_corr[1:7,2])
rownames(trends)<-gsub("Non.Fol","Non",rownames(trends))
trends<-data.frame(trends)
trends$Categories<-rownames(trends)
residuals<-data.frame(Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,residuals=ECV.BoM.BM$beta_primary$residuals_bias_corr)

#trends<-data.frame(trends%>%group_by(Categories)%>%mutate(pred.ECV=slope[1]*log.BoM.grand.mean+Trends))


```

Setup for Scaling Data to grand mean
```{r}
BoM.category.data<-data.frame(BrBo.Diet.DC.GS.SS.AP.trdata$dat,Categories=as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)))

BoM.category.data<-data.frame(BoM.category.data,Genus_Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label)

BoM.category.data$Categories<-gsub("Non.Fol","Non",BoM.category.data$Categories)
BoM.category.data$Categories<-gsub("Folivorous","Fol",BoM.category.data$Categories)

BoM.category.data
#################################
```

Scaling Species Data
```{r}

BoM.category.data$Residuals<-residuals$residuals[match(BoM.category.data$Genus_Species,residuals$Species)]

BoM.category.data$Trends<-trends$Trends[match(BoM.category.data$Categories,trends$Categories)]



```


```{r}
#Reorder Rows to match categories  
#BoM.category.data<-BoM.category.data%>%arrange(factor(Categories,levels=single.regimes))
#Turn your 'treatment' column into a character vector
BoM.category.data$Categories <- as.character(BoM.category.data$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.data$Categories <- factor(BoM.category.data$Categories, levels=single.regimes)

#Turn your 'treatment' column into a character vector
trends$Categories <- as.character(trends$Categories)
#Then turn it back into a factor with the levels in the correct order
trends$Categories <- factor(trends$Categories, levels=single.regimes)


```


Plot on Log Scale - using residuals
```{r}
meanLogBrainECV <- mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean))
scaleFUN <- function(x){sprintf("%.0f", round(exp(x + meanLogBrainECV), 1))}


library(scales)
show_col(reg.colors)

error.bar.type<-c(4,4,1,1,1,1,1)

labels<-c("FPG","FHP","NFSP","NFM","NFP","NFPG","NFHP")

#################
ms.plot<-ggplot(data=trends,aes(x=Categories,y=Trends))+
  geom_jitter(BoM.category.data,mapping=aes(x=Categories,y=Residuals,fill=Categories,shape=Categories),size=2.5,color="white",alpha=0.5,width=0.1)+
  geom_errorbar(aes(ymin=Trends-SE,ymax=Trends+SE),width=0.2,linetype=1)+
  geom_point(data=trends,mapping=aes(fill=Categories,shape=Categories),size=5,color="white")+ggtitle("Haplorhines")
  
ms.plot<-ms.plot+xlab("Diet + Mating System")+ylab("Endocranial Volume (cc)")

#Add extant species to plot
#ms.plot<-ms.plot+geom_point(BoM.category.data,mapping=aes(x=Categories,y=log(ECV.species.mean),fill=Categories),pch=21,size=2,color="white",position="jitter",alpha=0.5)

                                          
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=10),legend.text=element_text(size=12),
axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=10),
#plot.margin=unit(c(5.5,5.5,5.5,40),"points"),

#In the case it's helpful to anyone else, here are the arguments to margin (denoting to which side each value corresponds): margin(t = 0, r = 0, b = 0, l = 0, unit = "pt") – Joshua Rosenberg Mar 20 '18 at 0:14


# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)
ms.plot<-ms.plot+

scale_fill_manual(values=reg.colors[c(4,5,1,2,3,4,5)],name="Diet + Mating System",labels=single.regimes)+
scale_shape_manual(values=fol.shapes[c(2,2,1,1,1,1,1)],name="Diet + Mating System",labels=single.regimes)


#ms.plot<-ms.plot+scale_fill_manual(values=reg.colors)
ms.plot<-ms.plot+theme(legend.position = "none")
ms.plot<-ms.plot+scale_x_discrete(labels=c(labels))
ms.plot <- ms.plot + scale_y_continuous(labels = scaleFUN)

ms.plot

#5X5
```



###############
##Strepsirrhines
```{r}
rm(list=ls())

load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/Runs for Fig 2 091522/Strepsirrhines/SBR2 - WS from Strepsirrhines - Fig 2.RData")
```


#######
Fig. S7b: MS + AP Reconstructions Phylogeny
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),factor(internal.regimes.ms.ap[1:27]))

levels(regimes)

regimes <- factor(regimes, levels = c("Spatial Polygyny Nocturnal","Monogamy Nocturnal","Monogamy Diurnal","Polygynandry Diurnal"))

edge_regimes <- factor(regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])

reg.colors<-pal_aaas()(length(unique(regimes)))

show_col(reg.colors)

###################

plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge_regimes],edge.width = 1.75, cex = 0.5)
#6X5
```


Fig. S10a: Diet Categories + MS Reconstructions Regression Plot
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)))

regimes <- factor(regimes, levels = c("Spatial Polygyny Nocturnal","Monogamy Nocturnal","Monogamy Diurnal","Polygynandry Diurnal"))


#############
test<-ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients
#rownames(test)<-gsub("Fol","Folivorous",rownames(test))
#rownames(test)<-gsub("Non","Non-folivorous",rownames(test))


intercepts<-test[match(levels(regimes),rownames(test)),]
intercepts
#reg.colors<-pal_aaas()(length(unique(reordered.regimes)))
slope<-ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients[5]

```


```{r}
ms.plot<-ggplot(BrBo.Diet.DC.GS.SS.AP.trdata$dat,aes(y=log(ECV.species.mean),x=log(Body.mass.species.mean),fill=regimes))

ms.plot<-ms.plot+geom_point(size=3.5,color="white",pch=21) 
ms.plot<-ms.plot+xlab("log Body Mass (g)")+ylab("log Endocranial Volume (cc)")
                                     ms.plot<-ms.plot+theme(axis.text=element_text(size=16),axis.title=element_text(size=16),legend.title=element_text(size=10),legend.text=element_text(size=12),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),
panel.border = element_rect(colour = "black", fill=NA, size=0.5)
#,legend.position="none"
)
ms.plot<-ms.plot+theme(legend.key = element_rect(fill = "white"),legend.title = element_text(size=14))
#+scale_x_continuous(expand=c(0.5,0))


ms.plot<-ms.plot+geom_abline(intercept = intercepts[1,1],slope=slope,color=reg.colors[1],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[2,1],slope=slope,color=reg.colors[2],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[3,1],slope=slope,color=reg.colors[3],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[4,1],slope=slope,color=reg.colors[4],linetype=1,size=0.75)

ms.plot<-ms.plot+
scale_fill_manual(values=reg.colors,name="Mating System + \nActivity Period",labels=row.names(intercepts))

#ms.plot<-ms.plot+guides(fill = guide_legend(override.aes = list(size=5)))
ms.plot

#6 X 9 Small Pdf
#8 X 12, large PDF
#library(plotly)
#ggplotly()
```



```{r}
detach("package:plyr", unload=TRUE)
```

```{r}
library(dplyr)

single.regimes <-c("Spatial Polygyny Nocturnal","Monogamy Nocturnal","Monogamy Diurnal","Polygynandry Diurnal")

#log.BoM.grand.mean<-mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean))

trends<-ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients_bias_corr[1:4,1]
slope<-ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients_bias_corr[5,]
trends<-cbind("Trends"=trends,SE=ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients_bias_corr[1:4,2])
rownames(trends)<-gsub("Non.Fol","Non",rownames(trends))
trends<-data.frame(trends)
trends$Categories<-rownames(trends)
residuals<-data.frame(Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,residuals=ECV.BoM.BM$beta_primary$residuals_bias_corr)



```

Setting up Species Level Dataset
```{r}
BoM.category.data<-data.frame(BrBo.Diet.DC.GS.SS.AP.trdata$dat,Categories=as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)))

BoM.category.data<-data.frame(BoM.category.data,Genus_Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label)

BoM.category.data$Categories<-gsub("Non.Fol","Non",BoM.category.data$Categories)
BoM.category.data$Categories<-gsub("Folivorous","Fol",BoM.category.data$Categories)

BoM.category.data
#################################
```

Scaling Species Data
```{r}
BoM.category.data$Residuals<-residuals$residuals[match(BoM.category.data$Genus_Species,residuals$Species)]
BoM.category.data$Trends<-trends$Trends[match(BoM.category.data$Categories,trends$Categories)]

#Reorder Rows to match categories  
#Turn your 'treatment' column into a character vector
BoM.category.data$Categories <- as.character(BoM.category.data$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.data$Categories <- factor(BoM.category.data$Categories, levels=single.regimes)

#Turn your 'treatment' column into a character vector
trends$Categories <- as.character(trends$Categories)
#Then turn it back into a factor with the levels in the correct order
trends$Categories <- factor(trends$Categories, levels=single.regimes)


```


Plot on Log Scale - using residuals
```{r}
meanLogBrainECV <- mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean))
scaleFUN <- function(x){sprintf("%.0f", round(exp(x + meanLogBrainECV), 1))}

library(scales)
show_col(reg.colors)

labels<-c("SPN","MN","MD","PGD")

#################
ms.plot<-ggplot(data=trends,aes(x=Categories,y=Trends))+
  geom_jitter(BoM.category.data,mapping=aes(x=Categories,y=Residuals,fill=Categories),shape=21,size=2.5,color="white",alpha=0.5,width=0.1)+
  geom_errorbar(aes(ymin=Trends-SE,ymax=Trends+SE),width=0.2,linetype=1)+
  geom_point(data=trends,mapping=aes(fill=Categories),shape=21,size=5,color="white")+
  ggtitle("Strepsirrhines")

ms.plot<-ms.plot+xlab("Mating System + Activity Period")+ylab("Endocranial Volume (cc)")
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=10),legend.text=element_text(size=12),
axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=10),

#In the case it's helpful to anyone else, here are the arguments to margin (denoting to which side each value corresponds): margin(t = 0, r = 0, b = 0, l = 0, unit = "pt") – Joshua Rosenberg Mar 20 '18 at 0:14

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)

ms.plot<-ms.plot+scale_fill_manual(values=reg.colors,name="Mating System + Activity Period",labels=single.regimes)
ms.plot<-ms.plot+theme(legend.position = "none")
ms.plot<-ms.plot+scale_x_discrete(labels=c(labels))
ms.plot <- ms.plot + scale_y_continuous(labels = scaleFUN)

ms.plot

#5X5
```



############
Diet Categories

```{r}
library(dplyr)
library(ggsci)
library(ggplot2)
single.regimes <-c("Fol","Non")
reg.colors<-pal_aaas()(length(single.regimes))

#log.BoM.grand.mean<-mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean))

trends<-ECV.FoDCS.BoM.OUDF$beta_primary$coefficients_bias_corr[1:2,1]
slope<-ECV.FoDCS.BoM.OUDF$beta_primary$coefficients_bias_corr[3,]
trends<-cbind("Trends"=trends,SE=ECV.GS.MS.AP.BoM.BM$beta_primary$coefficients_bias_corr[1:2,2])
rownames(trends)<-gsub("Non.Fol","Non",rownames(trends))
trends<-data.frame(trends)
trends$Categories<-rownames(trends)
residuals<-data.frame(Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,residuals=ECV.BoM.BM$beta_primary$residuals_bias_corr)



```

Setting up Species Level Dataset
```{r}
BoM.category.data<-data.frame(BrBo.Diet.DC.GS.SS.AP.trdata$dat,Categories=as.factor(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict))

BoM.category.data<-data.frame(BoM.category.data,Genus_Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label)

BoM.category.data$Categories<-gsub("Non.Fol","Non",BoM.category.data$Categories)
BoM.category.data$Categories<-gsub("Folivorous","Fol",BoM.category.data$Categories)

BoM.category.data
#################################
```

Scaling Species Data
```{r}
BoM.category.data$Residuals<-residuals$residuals[match(BoM.category.data$Genus_Species,residuals$Species)]
BoM.category.data$Trends<-trends$Trends[match(BoM.category.data$Categories,trends$Categories)]

#Reorder Rows to match categories  
#Turn your 'treatment' column into a character vector
BoM.category.data$Categories <- as.character(BoM.category.data$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.data$Categories <- factor(BoM.category.data$Categories, levels=single.regimes)

#Turn your 'treatment' column into a character vector
trends$Categories <- as.character(trends$Categories)
#Then turn it back into a factor with the levels in the correct order
trends$Categories <- factor(trends$Categories, levels=single.regimes)


```


Plot on Log Scale - using residuals
```{r}
meanLogBrainECV <- mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean))
scaleFUN <- function(x){sprintf("%.0f", round(exp(x + meanLogBrainECV), 1))}

library(scales)
show_col(reg.colors)

labels<-c("Folivorous","Non-folivorous")

#################
ms.plot<-ggplot(data=trends,aes(x=Categories,y=Trends))+
  geom_jitter(BoM.category.data,mapping=aes(x=Categories,y=Residuals,fill=Categories),shape=21,size=2.5,color="white",alpha=0.5,width=0.1)+
  geom_errorbar(aes(ymin=Trends-SE,ymax=Trends+SE),width=0.2,linetype=1)+
  geom_point(data=trends,mapping=aes(fill=Categories),shape=21,size=5,color="white")+
  ggtitle("Strepsirrhines")

ms.plot<-ms.plot+xlab("Diet Categories")+ylab("Endocranial Volume (cc)")
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=10),legend.text=element_text(size=12),
axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=10),

#In the case it's helpful to anyone else, here are the arguments to margin (denoting to which side each value corresponds): margin(t = 0, r = 0, b = 0, l = 0, unit = "pt") – Joshua Rosenberg Mar 20 '18 at 0:14

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)

ms.plot<-ms.plot+scale_fill_manual(values=reg.colors,name="Diet Categories",labels=single.regimes)
ms.plot<-ms.plot+theme(legend.position = "none")
ms.plot<-ms.plot+scale_x_discrete(labels=c(labels))
ms.plot <- ms.plot + scale_y_continuous(labels = scaleFUN)

ms.plot

#5X5
```


######################
##Platyrrhines
```{r}
rm(list=ls())

#Load workspace
load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/Runs for Fig 2 091522/Platyrrhines/SBR2 - WS from Platyrrhines - Fig 2.RData")
```


Fig. S10b: Diet Categories + MS Reconstructions Phylogeny
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),factor(internal.regimes.FoDCS.ms))

#regimes<-internal.regimes.FoDC.ms.ap

#regimes <- factor(regimes, levels = c("Folivorous Spatial Polygyny Nocturnal","Folivorous Monogamy Nocturnal","Folivorous Monogamy Diurnal","Folivorous Polygynandry Diurnal","Folivorous Harem Polygyny Diurnal","Non-folivorous Spatial Polygyny Nocturnal","Non-folivorous Spatial Polygyny Diurnal","Non-folivorous Monogamy Nocturnal","Non-folivorous Monogamy Diurnal","Non-folivorous Polyandry Diurnal","Non-folivorous Polygynandry Diurnal", "Non-folivorous Harem Polygyny Diurnal"))

regimes<-gsub("Non.Fol","Non",regimes)
sub.regimes<-substring(regimes,5)

fol.regimes<-substring(regimes,1,3)

sub.regimes <- factor(sub.regimes, levels = c("Monogamy","Polyandry","Polygynandry","Harem Polygyny"))

levels(sub.regimes)

reg.colors<-pal_aaas()(length(unique(sub.regimes)))

show_col(reg.colors)


###################

edge.regimes <- factor(sub.regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])
fol.edge.regimes <- as.numeric(factor(fol.regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]]))


#edge.regimes <-factor(sub.regimes)
#fol.edge.regimes <- as.numeric(factor(fol.regimes))
#BrBo.Diet.DC.GS.SS.AP.trdata

#plot(BrBo.Diet.DC.GS.SS.trdata$phy,edge.color = reg.colors[edge.regimes], edge.width = 1.75, cex = 0.3) #10X12
fol.edge.regimes[fol.edge.regimes==1]<-6
fol.edge.regimes[fol.edge.regimes==2]<-1
#fol.edge.regimes[fol.edge.regimes==3]<-2
#fol.non.categories[fol.non.categories$BrBo.Diet.DC.GS.SS.trdata.dat.Fol.Non.Fol=="Non",1]<-1
#fol.non.categories[fol.non.categories$BrBo.Diet.DC.GS.SS.trdata.dat.Fol.Non.Fol!="Non",1]<-2
plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge.regimes], edge.lty = fol.edge.regimes,edge.width = 1.75, cex = 0.5)
#6X4
```


Fig. S10a: Diet Categories + MS Reconstructions Regression Plot
```{r}
regimes<-c(as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)))
levels(regimes)

regimes<-gsub("Non.Fol","Non",regimes)

regimes <- factor(regimes, levels = c("Fol Polygynandry","Fol Harem Polygyny","Non Monogamy","Non Polyandry","Non Polygynandry", "Non Harem Polygyny"))

sub.regimes<-substring(regimes,5)

fol.regimes<-substring(regimes,1,3)
fol.regimes <- factor(fol.regimes, levels = c("Non","Fol"))
fol.shapes<-c(21,22)

sub.regimes <- factor(sub.regimes, levels = c("Monogamy","Polyandry","Polygynandry","Harem Polygyny"))

levels(sub.regimes)

reg.colors<-pal_aaas()(length(unique(sub.regimes)))

show_col(reg.colors)

#############
test<-ECV.FoDCS.MS.BoM.OUDF$beta_primary$coefficients
#rownames(test)<-gsub("Fol","Folivorous",rownames(test))
rownames(test)<-gsub("Non.Fol","Non",rownames(test))

#rownames(test)<-gsub("Folivorous","Fol",rownames(test))


intercepts<-test[match(levels(regimes),rownames(test)),]
intercepts
#reg.colors<-pal_aaas()(length(unique(reordered.regimes)))
slope<-ECV.FoDCS.MS.BoM.OUDF$beta_primary$coefficients[7]



```


```{r}
ms.plot<-ggplot(BrBo.Diet.DC.GS.SS.AP.trdata$dat,aes(y=log(ECV.species.mean),x=log(Body.mass.species.mean),fill=regimes,shape=regimes))

ms.plot<-ms.plot+geom_point(size=3.5,color="white") 
ms.plot<-ms.plot+xlab("log Body Mass (g)")+ylab("log Endocranial Volume (cc)")
                                     ms.plot<-ms.plot+theme(axis.text=element_text(size=16),axis.title=element_text(size=16),legend.title=element_text(size=10),legend.text=element_text(size=12),

# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),
panel.border = element_rect(colour = "black", fill=NA, size=0.5)
#,legend.position="none"
)
ms.plot<-ms.plot+theme(legend.key = element_rect(fill = "white"),legend.title = element_text(size=14) )
#+scale_x_continuous(expand=c(0.5,0))


ms.plot<-ms.plot+geom_abline(intercept = intercepts[1,1],slope=slope,color=reg.colors[3],linetype=2,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[2,1],slope=slope,color=reg.colors[4],linetype=2,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[3,1],slope=slope,color=reg.colors[1],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[4,1],slope=slope,color=reg.colors[2],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[5,1],slope=slope,color=reg.colors[3],linetype=1,size=0.75)
ms.plot<-ms.plot+geom_abline(intercept = intercepts[6,1],slope=slope,color=reg.colors[4],linetype=1,size=0.75)

single.regimes<-c("Folivorous Polygynandry","Folivorous Harem Polygyny","Non-folivorous Monogamy","Non-folivorous Polyandry","Non-folivorous Polygynandry", "Non-folivorous Harem Polygyny")


#ms.plot<-ms.plot+labs(fill="Diet Categories+ \nMating System") #For famililes = shapes
ms.plot<-ms.plot+
scale_fill_manual(values=reg.colors[c(3,4,1,2,3,4)],name="Diet + Mating System",labels=single.regimes)+
scale_shape_manual(values=fol.shapes[c(2,2,1,1,1,1)],name="Diet + Mating System",labels=single.regimes)

#Diet Categories+ \nMating System+ \nActivity Period
#ms.plot<-ms.plot+guides(fill = guide_legend(override.aes = list(size=5)))
ms.plot

#6 X 9.5 Small Pdf
#8 X 12, large PDF
#library(plotly)
#ggplotly()
```


```{r}
detach("package:plyr", unload=TRUE)

```

```{r}
library(dplyr)

single.regimes<-c("Fol Polygynandry","Fol Harem Polygyny","Non Monogamy","Non Polyandry","Non Polygynandry", "Non Harem Polygyny")

log.BoM.grand.mean<-mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean))

trends<-ECV.FoDCS.MS.BoM.OUDF$beta_primary$coefficients_bias_corr[1:6,1]
slope<-ECV.FoDCS.MS.BoM.OUDF$beta_primary$coefficients_bias_corr[7,]
trends<-cbind("Trends"=trends,SE=ECV.FoDCS.MS.BoM.OUDF$beta_primary$coefficients_bias_corr[1:6,2])
rownames(trends)<-gsub("Non.Fol","Non",rownames(trends))
trends<-data.frame(trends)
trends$Categories<-rownames(trends)
residuals<-data.frame(Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,residuals=ECV.BoM.BM$beta_primary$residuals_bias_corr)

#trends<-data.frame(trends%>%group_by(Categories)%>%mutate(pred.ECV=slope[1]*log.BoM.grand.mean+Trends))

```

Setup for Species Level Data
```{r}
BoM.category.data<-data.frame(BrBo.Diet.DC.GS.SS.AP.trdata$dat,Categories=as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)))

BoM.category.data<-data.frame(BoM.category.data,Genus_Species=BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label)

BoM.category.data$Categories<-gsub("Non.Fol","Non",BoM.category.data$Categories)
BoM.category.data$Categories<-gsub("Folivorous","Fol",BoM.category.data$Categories)

BoM.category.data
#################################
```

Ading in residual and trend data to Species Level Data
```{r}
BoM.category.data$Residuals<-residuals$residuals[match(BoM.category.data$Genus_Species,residuals$Species)]
BoM.category.data$Trends<-trends$Trends[match(BoM.category.data$Categories,trends$Categories)]

```


```{r}
#Reorder Rows to match categories  
#BoM.category.data<-BoM.category.data%>%arrange(factor(Categories,levels=single.regimes))
#Turn your 'treatment' column into a character vector
BoM.category.data$Categories <- as.character(BoM.category.data$Categories)
#Then turn it back into a factor with the levels in the correct order
BoM.category.data$Categories <- factor(BoM.category.data$Categories, levels=single.regimes)

#Turn your 'treatment' column into a character vector
trends$Categories <- as.character(trends$Categories)
#Then turn it back into a factor with the levels in the correct order
trends$Categories <- factor(trends$Categories, levels=single.regimes)


```


Plot on Log Scale - using residuals
```{r}
meanLogBrainECV <- mean(log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean))
scaleFUN <- function(x){sprintf("%.0f", round(exp(x + meanLogBrainECV), 1))}


library(scales)
show_col(reg.colors)

labels<-c("FPG","FHP","NFM","NFP","NFPG","NFHP")

#################
ms.plot<-ggplot(data=trends,aes(x=Categories,y=Trends))+
  geom_jitter(BoM.category.data,mapping=aes(x=Categories,y=Residuals,fill=Categories,shape=Categories),size=2.5,color="white",alpha=0.5,width=0.1)+
  geom_errorbar(aes(ymin=Trends-SE,ymax=Trends+SE),width=0.2,linetype=1)+
  geom_point(data=trends,mapping=aes(fill=Categories,shape=Categories),size=5,color="white")+ggtitle("Platyrrhines")
  
ms.plot<-ms.plot+xlab("Diet + Mating System")+ylab("Endocranial Volume (cc)")

#Add extant species to plot
#ms.plot<-ms.plot+geom_point(BoM.category.data,mapping=aes(x=Categories,y=log(ECV.species.mean),fill=Categories),pch=21,size=2,color="white",position="jitter",alpha=0.5)

                                          
ms.plot<-ms.plot+theme(axis.text=element_text(size=12),axis.title=element_text(size=12),legend.title=element_text(size=10),legend.text=element_text(size=12),
axis.text.x = element_text(angle = 0,vjust=1,hjust=0.5,size=10),
#plot.margin=unit(c(5.5,5.5,5.5,40),"points"),

#In the case it's helpful to anyone else, here are the arguments to margin (denoting to which side each value corresponds): margin(t = 0, r = 0, b = 0, l = 0, unit = "pt") – Joshua Rosenberg Mar 20 '18 at 0:14


# Remove panel border
#panel.border = element_line("black"),
# Remove panel grid lines
panel.grid.major = element_line("gray95"),
panel.grid.minor = element_line("gray95"),
panel.background = element_blank(),

panel.border = element_rect(colour = "black", fill=NA, size=0.5),
plot.title = element_text(size=16)
#,legend.position="none"
)
ms.plot<-ms.plot+

scale_fill_manual(values=reg.colors[c(3,4,1,2,3,4)],name="Diet + Mating System",labels=single.regimes)+
scale_shape_manual(values=fol.shapes[c(2,2,1,1,1,1)],name="Diet + Mating System",labels=single.regimes)


#ms.plot<-ms.plot+scale_fill_manual(values=reg.colors)
ms.plot<-ms.plot+theme(legend.position = "none")
ms.plot<-ms.plot+scale_x_discrete(labels=c(labels))
ms.plot <- ms.plot + scale_y_continuous(labels = scaleFUN)

ms.plot

#5X5
```


