---
title: "Grabowski et al. - SBR2 - Bayou Setup - log Brain Size ~ log Body Size"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

All Primates Analysis
```{r}
rm(list=ls())
require(bayou)
library(treeplyr)
library(dplyr)
library(plyr)
options(scipen=999)
#For execution on a local, multicore CPU with excess RAM we recommend calling
options(mc.cores = parallel::detectCores())


```

Read in all data, including data on brain and body size with measurement error from Grabowski et al. (2016)

```{r}
#SB Revision 1 Tree
phylo.tree<-read.tree("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Tree/SB_Rv1_10K.tre")

#After renaming family to Callitrichidae - only change
brbo.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/ME Data/BrBo_means_predME_10192020_Callitri_tarsiers_step.csv")

diet.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/My Diet Data/Primate_Diet_Breakdown_100119.csv")

avg_GS.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New Group Size Data/Average.GS.DeCasien.Powell.041522.csv")

SS.data<-read.csv("/Volumes/GoogleDrive/My Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New SS Data/DeCasien MG Latest SS 041422.csv")


```

Drop tip for Chiropotes satanas to match original submission sample
```{r}
#which(phylo.tree$tip.label=="Chiropotes_satanas")
#length(phylo.tree$tip.label)
#phylo.tree<-drop.tip(phylo.tree,tip="Chiropotes_satanas")
#length(phylo.tree$tip.label)
```


Rescale to unit length
```{r}
l.tree<-max(branching.times(phylo.tree))
phylo.tree$edge.length<-phylo.tree$edge.length/l.tree ## rescale tree to height 1
max(branching.times(phylo.tree))

```


Get tree length
```{r}
phylo.tree <- multi2di(phylo.tree, random=FALSE)
phylo.tree$edge.length[phylo.tree$edge.length==0] <- .Machine$double.eps

#Reorder tree "postorder" to match bayou
phylo.tree<-reorder(phylo.tree,order = "postorder")
max(branching.times(phylo.tree))
```


Add on measurement error columns for Brain and Body Size
```{r}
#Brain/Body/Diet Data
brbo.data$N.species

brbo.data<-mutate(brbo.data,me.ECV.species=brbo.data$predict.sp.ln_ECV/brbo.data$N.species)
brbo.data<-mutate(brbo.data,me.BoM.species=brbo.data$predict.sp.ln_Body.mass/brbo.data$N.body.mass.species)

brbo.data<-mutate(brbo.data,me.ECV.females=brbo.data$predict.F.ln_ECV/brbo.data$N.female)
brbo.data<-mutate(brbo.data,me.BoM.females=brbo.data$predict.F.ln_Body.mass/brbo.data$N.body.mass.female)

brbo.data<-mutate(brbo.data,me.ECV.males=brbo.data$predict.M.ln_ECV/brbo.data$N.male)
brbo.data<-mutate(brbo.data,me.BoM.males=brbo.data$predict.M.ln_Body.mass/brbo.data$N.body.mass.male)
```

Split into Haplorhinnes vs. Strepsirrhines
```{r}
#brbo.data<-filter(brbo.data,Suborder=="Haplorrhini")
#brbo.data<-filter(brbo.data,Suborder=="Strepsirrhini")
#brbo.data<-filter(brbo.data,Parvorder=="Catarrhini")
#brbo.data<-filter(brbo.data,Parvorder=="Platyrrhini")

```

Max vy for body mass - add in upper range for vy
```{r}
#3* Variance of logged response is good upper range for vy says Kjetil, but too much in this case
max.vy<-var(log(brbo.data$Body.mass.species.mean),na.rm=TRUE)
max.hl<-max(branching.times(phylo.tree))
```

Diet Data, independently
```{r}
#Frug/Non Frug, Fol/Non Fol Diet Category Data
BrBo.diet.data<-merge(brbo.data,diet.data,by="Genus_Species")
dim(BrBo.diet.data)

BrBo.diet.trdata <- make.treedata(phylo.tree, BrBo.diet.data,name_column="Genus_Species")
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean)&!is.na(Frug.Non.Frug))

BrBo.diet.trdata<-filter(BrBo.diet.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean))

dim(BrBo.diet.trdata$dat)

#For original file with non-substuted males/females for species means
BrBo.diet.trdata<-filter(BrBo.diet.trdata, N.male>=1 & N.body.mass.male>=1 & N.female>=1 & N.body.mass.female>=1 & N.species>1 & N.body.mass.species>1)
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,N.species!="NA" & N.body.mass.species!="NA")

#BrBo.diet.trdata<-filter(BrBo.diet.trdata, N.species>=1 & N.body.mass.species>=1)
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,N.species!="NA" & N.body.mass.species!="NA")

dim(BrBo.diet.trdata$dat)

#write.table(BrBo.diet.trdata$dat,"test.csv",sep=",",row.names = FALSE)

```

Setup for Merged Data
Merged Brain/Body + Diet % + DC + GS + SS + AP, n=XX
```{r}
BrBo.Diet.GS.data<-merge(BrBo.diet.data,avg_GS.data,by="Genus_Species")
BrBo.Diet.GS.SS.data<-merge(BrBo.Diet.GS.data,SS.data,by="Genus_Species")

dim(BrBo.Diet.GS.SS.data)

BrBo.DC.GS.SS.AP.trdata <- make.treedata(phylo.tree, BrBo.Diet.GS.SS.data,name_column="Genus_Species")

BrBo.DC.GS.SS.AP.trdata<-filter(BrBo.DC.GS.SS.AP.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean)&!is.na(Combo.AGS)&!is.na(Social.System)&!is.na(Frug.Non.Frug))


BrBo.DC.GS.SS.AP.trdata<-filter(BrBo.DC.GS.SS.AP.trdata, N.male>=1 & N.body.mass.male>=1 & N.female>=1 & N.body.mass.female>=1 & N.species>1 & N.body.mass.species>1)

BrBo.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol<-revalue(BrBo.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol,c("Fol"="Folivorous","Non.Fol"="Non"))

BrBo.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug<-revalue(BrBo.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug,c("Frug"="Frugivorous","Non.Frug"="Non"))

dim(BrBo.DC.GS.SS.AP.trdata$dat)

```

Setup for bayou analysis
```{r}
#ECV
log.ECV.dat<-log(BrBo.DC.GS.SS.AP.trdata[['ECV.species.mean']])
me.ECV.species<-BrBo.DC.GS.SS.AP.trdata[['me.ECV.species']]

#Body Mass
log.BoM.dat<-log(BrBo.DC.GS.SS.AP.trdata[['Body.mass.species.mean']])
log.BoM.dat<-as.matrix(log.BoM.dat)
colnames(log.BoM.dat)<-"log.BoM.dat"
#log.BoM.dat<-t(log.BoM.dat)

me.BoM.species<-BrBo.DC.GS.SS.AP.trdata[['me.BoM.species']]

BrBo.DC.GS.SS.AP.tree<-BrBo.DC.GS.SS.AP.trdata$phy

```


```{r}
ntips <-length(BrBo.DC.GS.SS.AP.trdata$tip.label)
ntips
```


Save WS for bayou
```{r}
save.image("WS for bayou - SBR2 -128 sp 042422.RData")

```

