---
title: "Grabowski et al. - SBR2 - Bayou Analysis - log Brain Size ~ log Body Size"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
Setup for Bayou with Only log BoM as a predictor
From: Bayou - SBR2 - All Species 042722.Rmd

Species Only Analysis
```{r}
#Clear workspace
closeAllConnections() 
rm(list=ls())

library(slouch)
library(phytools)
library(treeplyr)
library(bayou)

library(doParallel)
library(treeplyr)

options(scipen=999)

#For execution on a local, multicore CPU with excess RAM we recommend calling
options(mc.cores = parallel::detectCores())

#First, load workspace for all data:
#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS for bayou - SBR1 - 040821.RData") #128 Species
```

Priors for bayou parameters
```{r}


param.alpha<-list(meanlog=log(0.05),sdlog=2)
param.sig2 <- list(scale=0.1)

param.beta_log.BoM.dat <- list(mean=0.6, sd=0.1)
param.k <- list(lambda=0.05*ntips, kmax=0.15*ntips)
param.sb=list(bmax=1, prob=1)
param.theta=list(mean=0, sd=1)

```

Placing priors on intercept and slope models using log normal distribution on alpha
```{r}
prior.BoM.11 <- make.prior(BrBo.DC.GS.SS.AP.tree, plot.prior = FALSE, 
                       dists=list(dalpha="dlnorm", dsig2="dhalfcauchy", dbeta_log.BoM.dat="dnorm",
                                  dsb="fixed", dk="fixed", dtheta="dnorm"), 
                       param=list(dalpha=param.alpha, dsig2=param.sig2,
                                  dbeta_log.BoM.dat=param.beta_log.BoM.dat,
                                  dtheta=param.theta),
                      #slopechange = "alphaWeighted", 
                       fixed=list(k=0, sb=numeric(0))
)

#No Shifts Allowed Prior
prior.BoM.N1.NS <- make.prior(BrBo.DC.GS.SS.AP.tree, plot.prior = FALSE, 
                       dists=list(dalpha="dlnorm", dsig2="dhalfcauchy", dbeta_log.BoM.dat="dnorm",
                                  dsb="fixed", dk="fixed", dtheta="dnorm"), 
                                  param=list(dalpha=param.alpha, dsig2=param.sig2,
                                  dbeta_log.BoM.dat=param.beta_log.BoM.dat,
                                  dtheta=param.theta),
                                  fixed=list(k=0, sb=numeric(0), loc=numeric(0), t2=numeric(0))

)


prior.BoM.N1 <- make.prior(BrBo.DC.GS.SS.AP.tree, plot.prior = FALSE, 
                       dists=list(dalpha="dlnorm", dsig2="dhalfcauchy", dbeta_log.BoM.dat="dnorm",
                                  dsb="dsb", dk="cdpois", dtheta="dnorm"), 
                                  param=list(dalpha=param.alpha, dsig2=param.sig2,
                                  dbeta_log.BoM.dat=param.beta_log.BoM.dat,
                                  dk=param.k,
                                  #dsb=list(bmax=terminal.branches, prob=1),
                                  dtheta=param.theta)
)

#No Shifts allowed Prior
prior.BoM.NN.NS <- make.prior(BrBo.DC.GS.SS.AP.tree, plot.prior = FALSE, 
                       dists=list(dalpha="dlnorm", dsig2="dhalfcauchy", dbeta_log.BoM.dat="dnorm",
                                  dsb="fixed", dk="fixed", dtheta="dnorm"), 
                                  param=list(dalpha=param.alpha, dsig2=param.sig2,
                                  dbeta_log.BoM.dat=param.beta_log.BoM.dat,
                                  dtheta=param.theta),
                                  fixed=list(k=0, sb=numeric(0), loc=numeric(0), t2=numeric(0))

)

prior.BoM.NN <- make.prior(BrBo.DC.GS.SS.AP.tree, plot.prior = FALSE, 
                       dists=list(dalpha="dlnorm", dsig2="dhalfcauchy", dbeta_log.BoM.dat="dnorm",
                                  dsb="dsb", dk="cdpois", dtheta="dnorm"), 
                                  param=list(dalpha=param.alpha, dsig2=param.sig2,
                                  dbeta_log.BoM.dat=param.beta_log.BoM.dat,
                                  dk=param.k,
                                  #dsb=list(bmax=terminal.branches, prob=1),
                                  dtheta=param.theta)
)
```

Manually set tuning parameters, and make the models. 
```{r}
#log Normal dist on alpha - param.theta=list(mean=0, sd=1)

#SB R1 Runs - 128 sp
#BoM.D11 = list(alpha=8.0, sig2=1.5, beta_log.BoM.dat=0.2,k=0.5, theta=1.5, slide=1) #Checked 040821
#BoM.DN1 = list(alpha=3.50, sig2=1.8, beta_log.BoM.dat=0.15,k=0.5, theta=8.9, slide=1) #Checked 040821
#BoM.DNN = list(alpha=6.3, sig2=1.4, beta_log.BoM.dat=0.20,k=c(1,1), theta=6.1, slide=1) #Edited 040821

#SB R2 Runs - 128 sp
#BoM.D11 = list(alpha=14.0, sig2=1.5, beta_log.BoM.dat=0.2,k=0.5, theta=1.6, slide=1) #Checked 042422
#BoM.DN1 = list(alpha=14, sig2=1.8, beta_log.BoM.dat=0.15,k=0.5, theta=2, slide=1) #Checked 042422
#BoM.DNN = list(alpha=15, sig2=1.4, beta_log.BoM.dat=0.20,k=c(1,1), theta=2, slide=1) #Edited 042422




```

Make bayou models 
```{r}
#########0###

#Model with BoM as Predictor, Fixed Intercept, Fixed Slope
model.BoM.11 <- makeBayouModel(log.ECV.dat ~ log.BoM.dat, rjpars = c(), 
                           tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat,
                           SE=sqrt(me.ECV.species), prior=prior.BoM.11, D=BoM.D11)


#NO SHIFTS - Model with BoM as Predictor, Random Intercept, Fixed Slope
model.BoM.N1.NS <- makeBayouModel(log.ECV.dat ~ log.BoM.dat, rjpars = c("theta"), 
                           tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat,
                           SE=sqrt(me.ECV.species), prior=prior.BoM.N1.NS, D=BoM.DN1)

#Model with BoM as Predictor, Random Intercept, Fixed Slope
model.BoM.N1 <- makeBayouModel(log.ECV.dat ~ log.BoM.dat, rjpars = c("theta"), 
                           tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat,
                           SE=sqrt(me.ECV.species), prior=prior.BoM.N1, D=BoM.DN1)


#NO SHIFTS - Model with BoM as Predictor, Random Intercept, Random Slope
model.BoM.NN.NS <- makeBayouModel(log.ECV.dat ~ log.BoM.dat, rjpars = 
                          c("theta","log.BoM.dat"),
                          tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat,
                          SE=sqrt(me.ECV.species), prior=prior.BoM.NN.NS, D=BoM.DNN)


#Model with BoM as Predictor, Random Intercept, Random Slope
model.BoM.NN <- makeBayouModel(log.ECV.dat ~ log.BoM.dat, rjpars = 
                          c("theta","log.BoM.dat"),
                          tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat,
                          SE=sqrt(me.ECV.species), prior=prior.BoM.NN, D=BoM.DNN)
```


No Shifts - First 10K
For log normal on alphas
```{r}
## Make MCMC objects:
mcmc.BoM.11.ch1 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.11$model, prior=prior.BoM.11, startpar=model.BoM.11$startpar, outname="modelBoM_11_r001", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#BoM as predictor, Fixed Intercept, Fixed Slope
mcmc.BoM.11.ch2 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.11$model, prior=prior.BoM.11, startpar=model.BoM.11$startpar, outname="modelBoM_11_r002", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

##### No Shifts first 10K
#BoM as predictor, Random Intercept, Fixed Slope - No Shifts first 10K
mcmc.BoM.N1.ch1 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.N1.NS$model, prior=prior.BoM.N1.NS, startpar=model.BoM.N1.NS$startpar, outname="modelBoM_N1_r001", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")


#BoM as predictor, Random Intercept, Fixed Slope - No Shifts first 10K
mcmc.BoM.N1.ch2 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.N1.NS$model, prior=prior.BoM.N1.NS, startpar=model.BoM.N1.NS$startpar, outname="modelBoM_N1_r002", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#BoM as predictor, Random Intercept, Random Slope - No shifts first 10K
mcmc.BoM.NN.ch1 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.NN.NS$model, prior=prior.BoM.NN.NS, startpar=model.BoM.NN.NS$startpar, outname="modelBoM_NN_r001", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")


#BoM as predictor, Random Intercept, Random Slope - No shifts first 10K
mcmc.BoM.NN.ch2 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.NN.NS$model, prior=prior.BoM.NN.NS, startpar=model.BoM.NN.NS$startpar, outname="modelBoM_NN_r002", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

```

Run models: #First 10K generations run with prior that does not allow shifts (NS)
```{r}
registerDoParallel(cores=8)
######################
ngens<-10000
mcmc.BoM.11.ch1$run(ngens)
mcmc.BoM.N1.ch1$run(ngens)
mcmc.BoM.NN.ch1$run(ngens)

mcmc.BoM.11.ch2$run(ngens)
mcmc.BoM.N1.ch2$run(ngens)
mcmc.BoM.NN.ch2$run(ngens)


```
Runs to tweak tuning parameters and run full models - with shifts allowed.
```{r}
## Make MCMC objects:
mcmc.BoM.11.ch1 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.11$model, prior=prior.BoM.11, startpar=model.BoM.11$startpar, outname="modelBoM_11_r001", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#BoM as predictor, Fixed Intercept, Fixed Slope
mcmc.BoM.11.ch2 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.11$model, prior=prior.BoM.11, startpar=model.BoM.11$startpar, outname="modelBoM_11_r002", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#############################################
#####With Shifts - for After 10K
#BoM as predictor, Random Intercept, Fixed Slope
mcmc.BoM.N1.ch1 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.N1$model, prior=prior.BoM.N1, startpar=model.BoM.N1$startpar, outname="modelBoM_N1_r001", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#BoM as predictor, Random Intercept, Fixed Slope
mcmc.BoM.N1.ch2 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.N1$model, prior=prior.BoM.N1, startpar=model.BoM.N1$startpar, outname="modelBoM_N1_r002", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#BoM as predictor, Random Intercept, Random Slope
mcmc.BoM.NN.ch1 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.NN$model, prior=prior.BoM.NN, startpar=model.BoM.NN$startpar, outname="modelBoM_NN_r001", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#BoM as predictor, Random Intercept, Random Slope
mcmc.BoM.NN.ch2 <- bayou.makeMCMC(tree=BrBo.DC.GS.SS.AP.tree, dat=log.ECV.dat, pred=log.BoM.dat, SE=sqrt(me.ECV.species), model=model.BoM.NN$model, prior=prior.BoM.NN, startpar=model.BoM.NN$startpar, outname="modelBoM_NN_r002", plot.freq=NULL,ticker.freq=2000, samp = 100,file.dir="/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System - Moved to Mac Pro GD/SB Revision 2/Results/bayou Results")

#####
```
Run Models
```{r}
registerDoParallel(cores=8)
######################
ngens<-30000 #Run to tweak tuning parameters

mcmc.BoM.11.ch1$run(ngens)
mcmc.BoM.N1.ch1$run(ngens)
mcmc.BoM.NN.ch1$run(ngens)

######################
```

```{r}
#############################################
#Now go up and change to shifts allowed prior, run rest with allowed shifts
registerDoParallel(cores=8)
#######################################
#ngens<-2990000
ngens<-3000000
mcmc.BoM.11.ch1$run(ngens)
mcmc.BoM.N1.ch1$run(ngens)
mcmc.BoM.NN.ch1$run(ngens)
mcmc.BoM.11.ch2$run(ngens)
mcmc.BoM.N1.ch2$run(ngens)
mcmc.BoM.NN.ch2$run(ngens)


chain.BoM.11.ch1 <- set.burnin(mcmc.BoM.11.ch1$load(saveRDS=TRUE), 0.3)
chain.BoM.N1.ch1 <- set.burnin(mcmc.BoM.N1.ch1$load(saveRDS=TRUE), 0.3)
chain.BoM.NN.ch1 <- set.burnin(mcmc.BoM.NN.ch1$load(saveRDS=TRUE), 0.3)

chain.BoM.11.ch2 <- set.burnin(mcmc.BoM.11.ch2$load(saveRDS=TRUE), 0.3)
chain.BoM.N1.ch2 <- set.burnin(mcmc.BoM.N1.ch2$load(saveRDS=TRUE), 0.3)
chain.BoM.NN.ch2 <- set.burnin(mcmc.BoM.NN.ch2$load(saveRDS=TRUE), 0.3)

#save.image("~/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/WS from bayou - SBR1 - 128 sp - 051721.RData")

#save.image("WS from bayou - SBR2 - 129 sp - tree 73 Ma 042722.RData") 


```

Set burnin and look at results
```{r}

summary(chain.BoM.11.ch1)
plot(chain.BoM.11.ch1)

summary(chain.BoM.N1.ch1)
plot(chain.BoM.N1.ch1)

summary(chain.BoM.NN.ch1)
plot(chain.BoM.NN.ch1)

summary(chain.BoM.11.ch2)
plot(chain.BoM.11.ch2)

summary(chain.BoM.N1.ch2)
plot(chain.BoM.N1.ch2)

summary(chain.BoM.NN.ch2)
  plot(chain.BoM.NN.ch2)

```

Look at results graphically
```{r}
par(mfrow=c(1,1))

plotSimmap.mcmc(chain.BoM.N1.ch1, lwd=2, show.tip.label=FALSE,pp.cutoff=0.3)
plotSimmap.mcmc(chain.BoM.N1.ch2, lwd=2, show.tip.label=FALSE,pp.cutoff=0.3)

plotSimmap.mcmc(chain.BoM.NN.ch1, lwd=2, show.tip.label=FALSE,pp.cutoff=0.3)
plotSimmap.mcmc(chain.BoM.NN.ch2, lwd=2, show.tip.label=FALSE,pp.cutoff=0.3)


```

Show all shifts with posterior probabilities greater than pp.cutoff = 0.2.
```{r}
phenogram.density(BrBo.DC.GS.SS.AP.tree, log.ECV.dat, chain=chain.BoM.N1.ch1, pp.cutoff=0.2)
phenogram.density(BrBo.DC.GS.SS.AP.tree, log.ECV.dat, chain=chain.BoM.N1.ch2, pp.cutoff=0.2)

phenogram.density(BrBo.DC.GS.SS.AP.tree, log.ECV.dat, chain=chain.BoM.NN.ch1, pp.cutoff=0.2)
phenogram.density(BrBo.DC.GS.SS.AP.tree, log.ECV.dat, chain=chain.BoM.NN.ch2, pp.cutoff=0.2)


```

Compare chains
```{r}

RlnL.12 <- gelman.R("lnL", chain1=chain.BoM.11.ch1, chain2=chain.BoM.11.ch2, plot=TRUE, type="n")
Ralpha.12 <- gelman.R("alpha", chain1=chain.BoM.11.ch1, chain2=chain.BoM.11.ch2, plot=TRUE, type="n")
Rsig2.12 <- gelman.R("sig2", chain1=chain.BoM.11.ch1, chain2=chain.BoM.11.ch2, plot=TRUE, type="n")

RlnL <- gelman.R("lnL", chain1=chain.BoM.N1.ch1, chain2=chain.BoM.N1.ch2, plot=TRUE, type="n", ylim=c(0.8, 1.2))
Ralpha <- gelman.R("alpha", chain1=chain.BoM.N1.ch1, chain2=chain.BoM.N1.ch2, plot=TRUE, type="n", ylim=c(0.95, 1.2))
Rsig2 <- gelman.R("sig2", chain1=chain.BoM.N1.ch1, chain2=chain.BoM.N1.ch2, plot=TRUE, type="n", ylim=c(0.95, 1.2))

L1 <- Lposterior(chain.BoM.N1.ch1,BrBo.DC.GS.SS.AP.tree, burnin=0.3)
L2 <- Lposterior(chain.BoM.N1.ch2,BrBo.DC.GS.SS.AP.tree, burnin=0.3)
plot(L1$pp,L2$pp, xlim=c(0,1), ylim=c(0,1), xlab="Chain 1", ylab="Chain 2")
curve(1*x, add=TRUE, lty=2)

RlnL <- gelman.R("lnL", chain1=chain.BoM.NN.ch1, chain2=chain.BoM.NN.ch2, plot=TRUE, type="n", ylim=c(0.95, 1.2))
Ralpha <- gelman.R("alpha", chain1=chain.BoM.NN.ch1, chain2=chain.BoM.NN.ch2, plot=TRUE, type="n", ylim=c(0.95, 1.2))
Rsig2 <- gelman.R("sig2", chain1=chain.BoM.NN.ch1, chain2=chain.BoM.NN.ch2, plot=TRUE, type="n", ylim=c(0.95, 1.2))


L1 <- Lposterior(chain.BoM.NN.ch1,BrBo.DC.GS.SS.AP.tree, burnin=0.3)
L2 <- Lposterior(chain.BoM.NN.ch2,BrBo.DC.GS.SS.AP.tree, burnin=0.3)
plot(L1$pp,L2$pp, xlim=c(0,1), ylim=c(0,1), xlab="Chain 1", ylab="Chain 2")
curve(1*x, add=TRUE, lty=2)


```

Combine chains and look at results
```{r}
chains.11 <- combine.chains(list(chain.BoM.11.ch1, chain.BoM.11.ch2), burnin.prop=0.3)

summary(chains.11)
quartz()
plot(chains.11)

chains.N1 <- combine.chains(list(chain.BoM.N1.ch1, chain.BoM.N1.ch2), burnin.prop=0.3)
summary(chains.N1)
plot(chains.N1)

chains.NN <- combine.chains(list(chain.BoM.NN.ch1, chain.BoM.NN.ch2), burnin.prop=0.3)
summary(chains.NN)
plot(chains.NN)

```

Compare different models by estimating marginal likelihoods using steppingstone function.
```{r}
library(doParallel)
registerDoParallel(cores=10)
Bk <- qbeta(seq(0,1, length.out=50), 0.3,1)
ngens<-10000
ss.11 <- mcmc.BoM.11.ch1$steppingstone(ngens, chains.11, Bk, burnin=0.3, plot=FALSE)
ss.N1 <- mcmc.BoM.N1.ch1$steppingstone(ngens, chains.N1, Bk, burnin=0.3, plot=FALSE)
ss.NN <- mcmc.BoM.NN.ch1$steppingstone(ngens, chains.NN, Bk, burnin=0.3, plot=FALSE)

mlnL <- c("11"=ss.11$lnr, "N1"=ss.N1$lnr, "NN"=ss.NN$lnr)
mlnL

#Bayes factor comparison
2*(ss.N1$lnr-ss.11$lnr)
2*(ss.N1$lnr-ss.NN$lnr)
2*(ss.11$lnr-ss.NN$lnr)
2*(ss.NN$lnr-ss.11$lnr)
2*(ss.NN$lnr-ss.N1$lnr)


plot(ss.11)
print(ss.11)
plot(ss.N1)
print(ss.N1)
plot(ss.NN)
print(ss.NN)


```


Store shifts and plot on phylogewny

```{r}
shiftsumsN1 <- shiftSummaries(chains.N1, mcmc.BoM.N1.ch1,pp.cutoff=0.4)#, burnin=0.3)
shiftsumsNN <- shiftSummaries(chains.NN, mcmc.BoM.NN.ch1, pp.cutoff=0.5)#, burnin=0.3)

plotShiftSummaries(shiftsumsN1)
plotShiftSummaries(shiftsumsNN)


shiftsumsN1$descendents
shiftsumsNN$descendents

shiftsumsN1$regressions
shiftsumsN1$regressions

pdf("ShiftSummaries.pdf", height=8, width=8)
plotShiftSummaries(shiftsumsN1)
dev.off()

```


Fig 1: Make Plots for Bayou
```{r}
library(ggsci)
#########################
par(mfrow=c(1,1))
par(bg = 'white')
cols<-viridis(4)

reg.colors<-pal_aaas(palette=c("default"),alpha=0.8)(9)
library(scales)
show_col(pal_aaas("default")(9))

#Posterior probabilities proportional to circle diameter:
pdf("Simmap_mcmc.pdf", height=6, width=4)

#No tip labels - main plot
plotSimmap.mcmc(chains.N1, cex=0.2,lwd=1.0,edge.type="regimes", pp.cutoff=0.5,circle.cex.max = 4.0,label.offset=1,pal = pal_aaas(),show.tip.label=FALSE)
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)

#With tip labels for SI
plotSimmap.mcmc(chains.N1, cex=0.2,lwd=1.0,edge.type="regimes", pp.cutoff=0.5,circle.cex.max = 4.0,label.offset=1,pal = pal_aaas(),show.tip.label=TRUE)
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)
 
#With edge labels
plotSimmap.mcmc(chains.N1, cex=0.2,lwd=1.0,edge.type="regimes",pp.cutoff=0.5,circle.cex.max = 1.0,circles=FALSE,pp.labels = TRUE,pp.cex=0.25)
edgelabels(cex=0.25,frame="none",adj=c(1,1))
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)

#Fig S1
plotBranchHeatMap(BrBo.DC.GS.SS.AP.tree, chains.N1, variable="theta",pal=cm.colors,cex=0.2)

dev.off()
#4X6 -Fig 1, then cut out

```


Fig S1
```{r}
#quartz()
par(mfrow=c(1,1))

plot(BrBo.DC.GS.SS.AP.tree,cex=0.1)
nodelabels(cex=0.25)

plot(chains.N1)

```

```{r}
library(ggsci)
#########################
par(mfrow=c(1,1))
par(bg = 'white')
cols<-viridis(4)

reg.colors<-pal_aaas(palette=c("default"),alpha=0.8)(9)
library(scales)
show_col(pal_aaas("default")(9))

#Posterior probabilities proportional to circle diameter:
pdf("Simmap_mcmc.pdf", height=6, width=4)

#No tip labels - main plot
plotSimmap.mcmc(chains.NN, cex=0.2,lwd=1.0,edge.type="regimes", pp.cutoff=0.5,circle.cex.max = 4.0,label.offset=1,pal = pal_aaas(),show.tip.label=FALSE)
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)

#With tip labels for SI
plotSimmap.mcmc(chains.NN, cex=0.2,lwd=1.0,edge.type="regimes", pp.cutoff=0.5,circle.cex.max = 4.0,label.offset=1,pal = pal_aaas(),show.tip.label=TRUE)
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)
 
#With edge labels
plotSimmap.mcmc(chains.NN, cex=0.2,lwd=1.0,edge.type="regimes",pp.cutoff=0.5,circle.cex.max = 1.0,circles=FALSE,pp.labels = TRUE,pp.cex=0.25)
edgelabels(cex=0.25,frame="none",adj=c(1,1))
axisPhylo(side=1,cex.axis=0.6,lwd=0.6)

#Fig S1
plotBranchHeatMap(BrBo.DC.GS.SS.AP.tree, chains.NN, variable="theta",pal=cm.colors,cex=0.2)

dev.off()


```


```{r}
write.table(slouch.output,"AllPrimates_Slouch_Table_04242022_woPW.csv",sep=",",row.names=FALSE)


```

