---
title: "SB R2 SIMMAP_ACE - All Primates - 062522 v1"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
All Primates Analysis

Run: SIMMAPS ACE 062522 v1
	Testing revised data from R2 but running original fitMk program, not parallel
	Gorilla g in strict classification is folivore
	Predictors:
		Fol.Non.Fol.Strict
		Fol.Non.Fol.Per
		Frug.Non.Frug.Per
		Social.System.DRclass
		Social.System.DGT
		Mating.System
		Activity.Period.DN
		GSC >50

	
```{r}
rm(list=ls())

####CHANGE
#Latest run
load("/Users/markgrabowski/Documents/Academic/Research/Current Projects/Brain Size Diet + Social System/SB Revision 2/Results/SIMMAPS 062522 v1/SIMMAPS/WS from SIMMAP - All Primates - Scaled 062522.RData")


library(phytools)
#devtools::install_github("kopperud/slouch",force=TRUE)

library(slouch)
library(ggsci)
library(treeplyr)
#library(bayou)
library(plyr)
#library(ape)
#library(viridis)
options(scipen=999)
library(parallel)

```


```{r}
#Just mating system
#reg.colors<-pal_npg()(length(unique(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN))))

#Mating system Only
#regimes<-c(as.character(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),as.character(internal.regimes.FoDCS.ssgt.ap))
#edge.regimes <- factor(regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])
#print(edge.regimes)
#print(reg.colors)
#plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge.regimes], edge.width = 1.75, cex = 0.00001)
#6X4 PDF
```


```{r}
#library(ggsci)

#Just mating system
#reg.colors<-pal_npg()(length(unique(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)))
#reg.colors<-pal_aaas()(length(unique(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)))

#Mating system Only
#regimes<-c(as.character(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System),as.character(internal.regimes.ms))
#edge.regimes <- factor(regimes[BrBo.Diet.DC.GS.SS.AP.trdata$phy$edge[,2]])
#print(edge.regimes)
##print(reg.colors)
#plot(BrBo.Diet.DC.GS.SS.AP.trdata$phy,edge.color = reg.colors[edge.regimes], edge.width = 1.75, cex = 0.00001)
#6X4 PDF
```


Summarize SIMMAP Discrete Character Mappings based on highest posterior probabilities with Activity Period
```{r}
## Extract the most likely regime for each internal node
## These have order n+1, n+2, n+3 ...
#internal_regimes_gs <- apply(reconstruction.gs$ace, #
#                               #1, 
#                               #function(e) colnames(reconstruction.gs$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.ssgt.ap<-summary(reconstruction.FoDCS.ssgt.ap)

internal.regimes.FoDCS.ssgt.ap<- apply(reconstruction.FoDCS.ssgt.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.ssgt.ap$ace)[which.max(e)])



#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.ssgt<-summary(reconstruction.FoDCS.ssgt)

internal.regimes.FoDCS.ssgt<- apply(reconstruction.FoDCS.ssgt$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.ssgt$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.ssgt.ap<-summary(reconstruction.FrDC.ssgt.ap)

internal.regimes.FrDC.ssgt.ap<- apply(reconstruction.FrDC.ssgt.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.ssgt.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.ssgt<-summary(reconstruction.FrDC.ssgt)

internal.regimes.FrDC.ssgt<- apply(reconstruction.FrDC.ssgt$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.ssgt$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDC.ssgt.ap<-summary(reconstruction.FoDC.ssgt.ap)

internal.regimes.FoDC.ssgt.ap<- apply(reconstruction.FoDC.ssgt.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.ssgt.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDC.ssgt<-summary(reconstruction.FoDC.ssgt)

internal.regimes.FoDC.ssgt<- apply(reconstruction.FoDC.ssgt$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.ssgt$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.ssgt.ap<-summary(reconstruction.ssgt.ap)

internal.regimes.ssgt.ap<- apply(reconstruction.ssgt.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.ssgt.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.ssgt<-summary(reconstruction.ssgt)

internal.regimes.ssgt<- apply(reconstruction.ssgt$ace, 
                               1, 
                               function(e) colnames(reconstruction.ssgt$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.gsc.ap<-summary(reconstruction.FoDCS.gsc.ap)

internal.regimes.FoDCS.gsc.ap<- apply(reconstruction.FoDCS.gsc.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.gsc.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.gsc<-summary(reconstruction.FoDCS.gsc)

internal.regimes.FoDCS.gsc<- apply(reconstruction.FoDCS.gsc$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.gsc$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.ss.ap<-summary(reconstruction.FoDCS.ss.ap)

internal.regimes.FoDCS.ss.ap<- apply(reconstruction.FoDCS.ss.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.ss.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.ss<-summary(reconstruction.FoDCS.ss)

internal.regimes.FoDCS.ss<- apply(reconstruction.FoDCS.ss$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.ss$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.ms.ap<-summary(reconstruction.FoDCS.ms.ap)

internal.regimes.FoDCS.ms.ap<- apply(reconstruction.FoDCS.ms.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.ms.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.ms<-summary(reconstruction.FoDCS.ms)

internal.regimes.FoDCS.ms<- apply(reconstruction.FoDCS.ms$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.ms$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS.ap<-summary(reconstruction.FoDCS.ap)

internal.regimes.FoDCS.ap<- apply(reconstruction.FoDCS.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FoDCS<-summary(reconstruction.FoDCS)

internal.regimes.FoDCS<- apply(reconstruction.FoDCS$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDCS$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.gsc.ap<-summary(reconstruction.FrDC.gsc.ap)

internal.regimes.FrDC.gsc.ap<- apply(reconstruction.FrDC.gsc.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.gsc.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.gsc<-summary(reconstruction.FrDC.gsc)

internal.regimes.FrDC.gsc<- apply(reconstruction.FrDC.gsc$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.gsc$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.ss.ap<-summary(reconstruction.FrDC.ss.ap)

internal.regimes.FrDC.ss.ap<- apply(reconstruction.FrDC.ss.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.ss.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.ss<-summary(reconstruction.FrDC.ss)

internal.regimes.FrDC.ss<- apply(reconstruction.FrDC.ss$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.ss$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.ms.ap<-summary(reconstruction.FrDC.ms.ap)

internal.regimes.FrDC.ms.ap<- apply(reconstruction.FrDC.ms.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.ms.ap$ace)[which.max(e)])


#Frugivore Diet Categories, group size categories, social system, activity pattern
reconstruction.FrDC.ms<-summary(reconstruction.FrDC.ms)

internal.regimes.FrDC.ms<- apply(reconstruction.FrDC.ms$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.ms$ace)[which.max(e)])



#Frugivore Diet Categories, group size categories, mating system, activity pattern
reconstruction.FoDC.gsc.ap<-summary(reconstruction.FoDC.gsc.ap)

internal.regimes.FoDC.gsc.ap<- apply(reconstruction.FoDC.gsc.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.gsc.ap$ace)[which.max(e)])

#####
#Frugivore Diet Categories, group size categories, activity pattern
reconstruction.FoDC.gsc<-summary(reconstruction.FoDC.gsc)

internal.regimes.FoDC.gsc <- apply(reconstruction.FoDC.gsc$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.gsc$ace)[which.max(e)])

#####
#Frugivore Diet Categories, social system, activity pattern
reconstruction.FoDC.ss.ap<-summary(reconstruction.FoDC.ss.ap)

internal.regimes.FoDC.ss.ap <- apply(reconstruction.FoDC.ss.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.ss.ap$ace)[which.max(e)])

#Frugivore Diet Categories, mating system, activity pattern
reconstruction.FoDC.ss<-summary(reconstruction.FoDC.ss)
internal.regimes.FoDC.ss<- apply(reconstruction.FoDC.ss$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.ss$ace)[which.max(e)])


#Group size categories, social system, activity pattern
reconstruction.FoDC.ms.ap<-summary(reconstruction.FoDC.ms.ap)
internal.regimes.FoDC.ms.ap <- apply(reconstruction.FoDC.ms.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.ms.ap$ace)[which.max(e)])

#Group size categories, mating system, activity pattern
reconstruction.FoDC.ms<-summary(reconstruction.FoDC.ms)
internal.regimes.FoDC.ms <- apply(reconstruction.FoDC.ms$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.ms$ace)[which.max(e)])

###############
#Folivore categories, Group size categories, social system, activity pattern
reconstruction.FoDC.ap<-summary(reconstruction.FoDC.ap)
internal.regimes.FoDC.ap<- apply(reconstruction.FoDC.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC.ap$ace)[which.max(e)])

#Folivore categories, Group size categories, Mating system, activity pattern
reconstruction.FoDC<-summary(reconstruction.FoDC)
internal.regimes.FoDC<- apply(reconstruction.FoDC$ace, 
                               1, 
                               function(e) colnames(reconstruction.FoDC$ace)[which.max(e)])




#####
#Folivore Diet Categories, Group Size Categories, Activity Pattern
reconstruction.FrDC.ap<-summary(reconstruction.FrDC.ap)
internal.regimes.FrDC.ap <- apply(reconstruction.FrDC.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC.ap$ace)[which.max(e)])

#####
#Folivore Diet Categories, Social System, Activity Pattern
reconstruction.FrDC<-summary(reconstruction.FrDC)
internal.regimes.FrDC <- apply(reconstruction.FrDC$ace, 
                               1, 
                               function(e) colnames(reconstruction.FrDC$ace)[which.max(e)])

#Folivore Diet Categories, Mating System, Activity Pattern
reconstruction.gsc.ap<-summary(reconstruction.gsc.ap)
internal.regimes.gsc.ap <- apply(reconstruction.gsc.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.gsc.ap$ace)[which.max(e)])

#########
#Frugivore Diet Categories, Activity Pattern
reconstruction.gsc<-summary(reconstruction.gsc)
internal.regimes.gsc <- apply(reconstruction.gsc$ace, 
                               1, 
                               function(e) colnames(reconstruction.gsc$ace)[which.max(e)])

#Folivore Diet Categories, Activity Pattern
reconstruction.ss.ap<-summary(reconstruction.ss.ap)
internal.regimes.ss.ap <- apply(reconstruction.ss.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.ss.ap$ace)[which.max(e)])


#Activity Pattern
########
reconstruction.ss<-summary(reconstruction.ss)
internal.regimes.ss <- apply(reconstruction.ss$ace, 
                               1, 
                               function(e) colnames(reconstruction.ss$ace)[which.max(e)])
########
reconstruction.ms.ap<-summary(reconstruction.ms.ap)
internal.regimes.ms.ap <- apply(reconstruction.ms.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.ms.ap$ace)[which.max(e)])
################
reconstruction.ms<-summary(reconstruction.ms)
internal.regimes.ms <- apply(reconstruction.ms$ace, 
                               1, 
                               function(e) colnames(reconstruction.ms$ace)[which.max(e)])


###############
reconstruction.ap<-summary(reconstruction.ap)
internal.regimes.ap <- apply(reconstruction.ap$ace, 
                               1, 
                               function(e) colnames(reconstruction.ap$ace)[which.max(e)])

```

Social System Group Types
Strict Folivore Models First

Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System GT + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ssgt.ap

ECV.FoDCS.GS.SSGT.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.SSGT.AP.BoM.OURDF)


  ECV.FoDCS.GS.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.GS.SSGT.AP.BoM.BM)



```

Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ssgt

ECV.FoDCS.GS.SSGT.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.GS.SSGT.BoM.OURDF)


  ECV.FoDCS.GS.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.SSGT.BoM.BM)



```



```{r}

######################
#Folivore Diet Categories + Social System GT + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ssgt.ap

  ECV.FoDCS.SSGT.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.SSGT.AP.BoM.OUDF)

  ECV.FoDCS.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.SSGT.AP.BoM.BM)



```



```{r}

######################
#Folivore Diet Categories + Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ssgt

  ECV.FoDCS.SSGT.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.SSGT.BoM.OUDF)

  ECV.FoDCS.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.SSGT.BoM.BM)




```

```{r}
######################
#Folivore Diet Categories Strict + Group Size Categories + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.gsc.ap

  ECV.FoDCS.GSC.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001,3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GSC.AP.BoM.OUDF)

  ECV.FoDCS.GSC.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GSC.AP.BoM.BM)



```

###################################

## Original DeCasien Sociality Categories

Diet Categories + ...
###########################

Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ss.ap

  ECV.FoDCS.GS.SS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.SS.AP.BoM.OURDF)


ECV.FoDCS.GS.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.SS.AP.BoM.BM)

######################
#Folivore Diet Categories + Group Size Continuous + Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ms.ap

  ECV.FoDCS.GS.MS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                                        fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.MS.AP.BoM.OURDF)


  ECV.FoDCS.GS.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                                                          random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
             
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.MS.AP.BoM.BM)

```

Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ss

ECV.FoDCS.GS.SS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.SS.BoM.OURDF)


  ECV.FoDCS.GS.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.GS.SS.BoM.BM)

######################
#Folivore Diet Categories + Group Size Continuous + Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ms

  ECV.FoDCS.GS.MS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.MS.BoM.OURDF)


  ECV.FoDCS.GS.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.MS.BoM.BM)

```


```{r}
######################
#Folivore Diet Categories + Group Size + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ap

  ECV.FoDCS.GS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          

                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.AP.BoM.OURDF)



  ECV.FoDCS.GS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.GS.AP.BoM.BM)

###########
######################
#Folivore Diet Categories + Social System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ss.ap

  ECV.FoDCS.SS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.SS.AP.BoM.OUDF)

  ECV.FoDCS.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.SS.AP.BoM.BM)

######################
#Folivore Diet Categories + Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ms.ap

ECV.FoDCS.MS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.MS.AP.BoM.OUDF)

  ECV.FoDCS.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.MS.AP.BoM.BM)


```


```{r}
######################
#Folivore Diet Categories + Group Size
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS

  ECV.FoDCS.GS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                 
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.GS.BoM.OURDF)



  ECV.FoDCS.GS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                 
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.GS.BoM.BM)

###########

#Folivore Diet Categories + Group Size Categories
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.gsc

  ECV.FoDCS.GSC.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.GSC.BoM.OUDF)

  ECV.FoDCS.GSC.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.GSC.BoM.BM)


######################
#Folivore Diet Categories + Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ss

  ECV.FoDCS.SS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.SS.BoM.OUDF)

  ECV.FoDCS.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.SS.BoM.BM)

######################
#Folivore Diet Categories + Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ms

  ECV.FoDCS.MS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.MS.BoM.OUDF)

  ECV.FoDCS.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.MS.BoM.BM)


```

```{r}
##############
#Folivore Diet Categories + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS.ap

  ECV.FoDCS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.AP.BoM.OUDF)

  ECV.FoDCS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.AP.BoM.BM)

```
XX
```{r}
##############
#Folivore Diet Categories
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDCS


  ECV.FoDCS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDCS.BoM.OUDF)

  ECV.FoDCS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Strict ,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDCS.BoM.BM)

```

```{r}
#save.image("WS from SIMMAPACE-All Primates - Slouch pt 1.RData")

```


Original Folivore Definition Models
```{r}
#Frugivore Diet Categories + Group Size Continuous + Social System GT + Activity Period
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ssgt.ap
ECV.FrDC.GS.SSGT.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
               
summary(ECV.FrDC.GS.SSGT.AP.BoM.OURDF)


ECV.FrDC.GS.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
      
summary(ECV.FrDC.GS.SSGT.AP.BoM.BM)



```


```{r}
#Frugivore Diet Categories + Group Size Continuous + Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ssgt

                      ECV.FrDC.GS.SSGT.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
summary(ECV.FrDC.GS.SSGT.BoM.OURDF)


                      ECV.FrDC.GS.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
             
summary(ECV.FrDC.GS.SSGT.BoM.BM)



```


```{r}

######################
#Frugivore Diet Categories + Social System GT + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ssgt.ap

ECV.FrDC.SSGT.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))

summary(ECV.FrDC.SSGT.AP.BoM.OUDF)

ECV.FrDC.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))

summary(ECV.FrDC.SSGT.AP.BoM.BM)


```


```{r}
######################
#Frugivore Diet Categories + Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ssgt

ECV.FrDC.SSGT.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
 
summary(ECV.FrDC.SSGT.BoM.OUDF)

ECV.FrDC.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))

summary(ECV.FrDC.SSGT.BoM.BM)


```

Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System GT + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ssgt.ap

  ECV.FoDC.GS.SSGT.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GS.SSGT.AP.BoM.OURDF)


  ECV.FoDC.GS.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GS.SSGT.AP.BoM.BM)



```

Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ssgt

  ECV.FoDC.GS.SSGT.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.SSGT.BoM.OURDF)


  ECV.FoDC.GS.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.SSGT.BoM.BM)



```



```{r}

######################
#Folivore Diet Categories + Social System GT + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ssgt.ap

ECV.FoDC.SSGT.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.SSGT.AP.BoM.OUDF)

ECV.FoDC.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.SSGT.AP.BoM.BM)



```


```{r}

######################
#Folivore Diet Categories + Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ssgt

  ECV.FoDC.SSGT.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.SSGT.BoM.OUDF)

  ECV.FoDC.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.SSGT.BoM.BM)




```


```{r}
#Average Group Size + Social System GT + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ssgt.ap

  ECV.GS.SSGT.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         

                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                    
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.SSGT.AP.BoM.OURDF)

            ECV.GS.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GS.SSGT.AP.BoM.BM)






```


```{r}
#Average Group Size + Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ssgt

ECV.GS.SSGT.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.SSGT.BoM.OURDF)

            ECV.GS.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.SSGT.BoM.BM)



```


Single Factors + AP   
```{r}
###########
#Social System GT + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ssgt.ap

  ECV.SSGT.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.SSGT.AP.BoM.OUDF)


  ECV.SSGT.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.SSGT.AP.BoM.BM)



```

Single Factors

```{r}
###########
#Social System GT
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ssgt

  ECV.SSGT.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SSGT.BoM.OUDF)


  ECV.SSGT.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DGT,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SSGT.BoM.BM)

```


###################################

## Original DeCasien Sociality Categories

Diet Categories + ...
###########################

```{r}
#Frugivore Diet Categories + Group Size Continuous + Social System + Activity Period
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ss.ap

                      ECV.FrDC.GS.SS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
      
summary(ECV.FrDC.GS.SS.AP.BoM.OURDF)


                      ECV.FrDC.GS.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
                      
summary(ECV.FrDC.GS.SS.AP.BoM.BM)

######################
#Frugivore Diet Categories + Group Size Continuous + Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ms.ap

ECV.FrDC.GS.MS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))

summary(ECV.FrDC.GS.MS.AP.BoM.OURDF)

                      ECV.FrDC.GS.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))

summary(ECV.FrDC.GS.MS.AP.BoM.BM)



```


```{r}
#Frugivore Diet Categories + Group Size Continuous + Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ss

                      ECV.FrDC.GS.SS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
                      
summary(ECV.FrDC.GS.SS.BoM.OURDF)


ECV.FrDC.GS.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
            
summary(ECV.FrDC.GS.SS.BoM.BM)

######################
#Frugivore Diet Categories + Group Size Continuous + Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ms

                      ECV.FrDC.GS.MS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
            
summary(ECV.FrDC.GS.MS.BoM.OURDF)


                      ECV.FrDC.GS.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
                      
summary(ECV.FrDC.GS.MS.BoM.BM)

```


```{r}
######################
#Frugivore Diet Categories + Group Size Continuous + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ap

                      ECV.FrDC.GS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                                     lower = c(0.0001, 0.0001))

summary(ECV.FrDC.GS.AP.BoM.OURDF)



                      ECV.FrDC.GS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                            fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
                 
summary(ECV.FrDC.GS.AP.BoM.BM)

###########
#Frugivore Diet Categories + Group Size Categories + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.gsc.ap

                      ECV.FrDC.GSC.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
summary(ECV.FrDC.GSC.AP.BoM.OUDF)

                      ECV.FrDC.GSC.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                            fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
          
summary(ECV.FrDC.GSC.AP.BoM.BM)


######################
#Frugivore Diet Categories + Social System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ss.ap

                      ECV.FrDC.SS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
            
summary(ECV.FrDC.SS.AP.BoM.OUDF)

                      ECV.FrDC.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
                
summary(ECV.FrDC.SS.AP.BoM.BM)

######################
#Frugivore Diet Categories + Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ms.ap

                      ECV.FrDC.MS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
        
summary(ECV.FrDC.MS.AP.BoM.OUDF)

                      ECV.FrDC.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                                                            fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
      
summary(ECV.FrDC.MS.AP.BoM.BM)

```


```{r}
######################
#Frugivore Diet Categories + Group Size Continuous
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC

                      ECV.FrDC.GS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                 
                              fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
          
summary(ECV.FrDC.GS.BoM.OURDF)



                      ECV.FrDC.GS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                 
                              fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
summary(ECV.FrDC.GS.BoM.BM)

###########
#Frugivore Diet Categories + Group Size Categories
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.gsc

                      ECV.FrDC.GSC.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
               
summary(ECV.FrDC.GSC.BoM.OUDF)

ECV.FrDC.GSC.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
                    
summary(ECV.FrDC.GSC.BoM.BM)


######################
#Frugivore Diet Categories + Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ss

                      ECV.FrDC.SS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
            
summary(ECV.FrDC.SS.BoM.OUDF)

ECV.FrDC.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))

summary(ECV.FrDC.SS.BoM.BM)

######################
#Frugivore Diet Categories + Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ms

                      ECV.FrDC.MS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
            
summary(ECV.FrDC.MS.BoM.OUDF)

                      ECV.FrDC.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              
                              lower = c(0.0001, 0.0001))
                      
summary(ECV.FrDC.MS.BoM.BM)

```

```{r}

#save.image("WS from SIMMAPACE-All Primates - Slouch pt 2.RData")
```


Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ss.ap

  ECV.FoDC.GS.SS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.SS.AP.BoM.OURDF)


  ECV.FoDC.GS.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.SS.AP.BoM.BM)

######################
#Folivore Diet Categories + Group Size Continuous + Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ms.ap

  ECV.FoDC.GS.MS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                                                                        fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GS.MS.AP.BoM.OURDF)


  ECV.FoDC.GS.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                                                          random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
             
                                                   fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per, BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.MS.AP.BoM.BM)

```

Folivore Non-Folivore Diet Categories
```{r}
#Folivore Diet Categories + Group Size Continuous + Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ss

  ECV.FoDC.GS.SS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GS.SS.BoM.OURDF)


  ECV.FoDC.GS.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GS.SS.BoM.BM)

######################
#Folivore Diet Categories + Group Size Continuous + Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ms

  ECV.FoDC.GS.MS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.MS.BoM.OURDF)


  ECV.FoDC.GS.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.MS.BoM.BM)

```


```{r}
######################
#Folivore Diet Categories + Group Size + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ap

  ECV.FoDC.GS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          

                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.AP.BoM.OURDF)



  ECV.FoDC.GS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GS.AP.BoM.BM)

######################
#Folivore Diet Categories + Group Size Categories + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.gsc.ap

  ECV.FoDC.GSC.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GSC.AP.BoM.OUDF)

  ECV.FoDC.GSC.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GSC.AP.BoM.BM)

######################
###########
######################
#Folivore Diet Categories + Social System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ss.ap

  ECV.FoDC.SS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.SS.AP.BoM.OUDF)

  ECV.FoDC.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

                                         fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.SS.AP.BoM.BM)

######################
#Folivore Diet Categories + Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ms.ap

  ECV.FoDC.MS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.MS.AP.BoM.OUDF)

  ECV.FoDC.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),

fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.MS.AP.BoM.BM)


```


```{r}
######################
#Folivore Diet Categories + Group Size
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC

  ECV.FoDC.GS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                 
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GS.BoM.OURDF)



  ECV.FoDC.GS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                 
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))

summary(ECV.FoDC.GS.BoM.BM)

###########

#Folivore Diet Categories + Group Size Categories
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.gsc

  ECV.FoDC.GSC.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GSC.BoM.OUDF)

  ECV.FoDC.GSC.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.GSC.BoM.BM)


######################
#Folivore Diet Categories + Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ss

  ECV.FoDC.SS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.SS.BoM.OUDF)

  ECV.FoDC.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.SS.BoM.BM)

######################
#Folivore Diet Categories + Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ms

  ECV.FoDC.MS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.MS.BoM.OUDF)

  ECV.FoDC.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                    species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                    response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                    mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                    mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                    hillclimb = TRUE,convergence = 150,
                    
                    lower = c(0.0001, 0.0001))
summary(ECV.FoDC.MS.BoM.BM)


```

```{r}
#Average Group Size + Social System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ss.ap

  ECV.GS.SS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         

                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                    
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GS.SS.AP.BoM.OURDF)

            ECV.GS.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                                         
                    fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.SS.AP.BoM.BM)



######################
#Average Group Size + Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ms.ap

  ECV.GS.MS.AP.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                                                            random.cov = 
                              log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                               fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.MS.AP.BoM.OURDF)

            ECV.GS.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),                                          
                      fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.MS.AP.BoM.BM)


```

```{r}
#Average Group Size + Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ss

  ECV.GS.SS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GS.SS.BoM.OURDF)

            ECV.GS.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GS.SS.BoM.BM)



######################
#Average Group Size + Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ms

  ECV.GS.MS.BoM.OURDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.MS.BoM.OURDF)

            ECV.GS.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                    fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GS.MS.BoM.BM)


```



#### Rerun Below
Single Factors + AP
```{r}
##############
#Frugivore Diet Categories + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC.ap

  ECV.FrDC.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FrDC.AP.BoM.OUDF)

  ECV.FrDC.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FrDC.AP.BoM.BM)


```

```{r}
##############
#Folivore Diet Categories + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC.ap

  ECV.FoDC.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.AP.BoM.OUDF)

  ECV.FoDC.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.FoDC.AP.BoM.BM)

```

Continuous Factors + AP
```{r}
############
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ap

  ECV.GS.AP.BoM.OURD<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),

                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GS.AP.BoM.OURD)


  ECV.GS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),

                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.AP.BoM.BM)

######################


```

```{r}
###########
#Group Size Categories + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.gsc.ap

  ECV.GSC.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GSC.AP.BoM.OUDF)


  ECV.GSC.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GSC.AP.BoM.BM)


```

```{r}
###########
#Social System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ss.ap

  ECV.SS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.SS.AP.BoM.OUDF)


  ECV.SS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.SS.AP.BoM.BM)


###########
#Mating System + AP
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ms.ap

  ECV.MS.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),

                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.MS.AP.BoM.OUDF)


  ECV.MS.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = as.factor(paste(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN)),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.MS.AP.BoM.BM)


```

Single Factors
```{r}
##############
#Frugivore Diet Categories
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FrDC

  ECV.FrDC.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FrDC.BoM.OUDF)

  ECV.FrDC.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Frug.Non.Frug.Per ,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FrDC.BoM.BM)


```

```{r}
##############
#Folivore Diet Categories
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.FoDC

  ECV.FoDC.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.BoM.OUDF)

  ECV.FoDC.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Fol.Non.Fol.Per ,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.FoDC.BoM.BM)

```

Continuous Factors
```{r}
############
#Group Size Continuous

ECV.GS.BoM.OURD<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.001, max.hl*3, length.out = 50),
                     vy_values = seq(0.001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.BoM.OURD)

ECV.GS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                    random.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Combo.AGS),
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     lower = c(0.0001, 0.0001))
summary(ECV.GS.BoM.BM)

######################


```

Activity Pattern
```{r}
###########
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ap

  ECV.AP.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.AP.BoM.OUDF)



  ECV.AP.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                     fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Activity.Period.DN,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.AP.BoM.BM)


```



```{r}
###########
#Group Size Categories
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.gsc

  ECV.GSC.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))
summary(ECV.GSC.BoM.OUDF)


  ECV.GSC.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Cat.group.size,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.GSC.BoM.BM)


```

```{r}
###########
#Social System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ss

  ECV.SS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SS.BoM.OUDF)


  ECV.SS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Social.System.DRclass,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.SS.BoM.BM)


###########
#Mating System
BrBo.Diet.DC.GS.SS.AP.trdata$phy$node.label <- internal.regimes.ms

  ECV.MS.BoM.OUDF<-slouch.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,
                     direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hl_values = seq(0.0001, max.hl*3, length.out = 50),
                     vy_values = seq(0.0001, 1, length.out = 50),
                     hillclimb = FALSE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.MS.BoM.OUDF)


  ECV.MS.BoM.BM<-brown.fit(BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                     species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                     response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                      fixed.fact = BrBo.Diet.DC.GS.SS.AP.trdata$dat$Mating.System,
                    direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                     mv.response = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                     mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                     hillclimb = TRUE,convergence = 150,
                     
                     lower = c(0.0001, 0.0001))

summary(ECV.MS.BoM.BM)


```




```{r}
#OU Model of Evolution
ECV.BoM.OU<-slouch.fit(phy = BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.0001, 0.0001))

summary(ECV.BoM.OU)


#BM Model of Evolution
ECV.BoM.BM<-brown.fit(phy = BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.0001, 0.0001))


summary(ECV.BoM.BM)

```

```{r}
#OU Model of Evolution
ECV.OU<-slouch.fit(phy = BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              mv.response=BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 10, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.0001, 0.0001))

summary(ECV.OU)


#BM Model of Evolution
ECV.BM<-brown.fit(phy = BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$ECV.species.mean),
                              mv.response=BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.ECV.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.0001, 0.0001))


summary(ECV.BM)

```

```{r}
#OU Model of Evolution
BoM.OU<-slouch.fit(phy = BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hl_values = seq(0.0001, max.hl*3, length.out = 50),
                              vy_values = seq(0.0001, 10, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.0001, 0.0001))

summary(BoM.OU)


#BM Model of Evolution
BoM.BM<-brown.fit(phy = BrBo.Diet.DC.GS.SS.AP.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.AP.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.AP.trdata$dat$Body.mass.species.mean),
                              mv.response=BrBo.Diet.DC.GS.SS.AP.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.0001, 0.0001))


summary(BoM.BM)

```

```{r}
#save.image("WS from SIMMAPACE-All Primates - Slouch pt 3.RData")
```



Strict Folivore Models First

```{r}

###################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SSGT.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1])
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SSGT.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

###################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SSGT.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SSGT.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


##################
slouch.output<-make.slouch.table(ECV.FoDCS.SSGT.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.SSGT.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDCS.SSGT.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.SSGT.BoM.BM,"FF.BM","Fol Diet Categories Strict+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

```


## Original DeCasien et al. 2017 Sociality Data - social system reclassified

```{r}
#Folivore
###################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SS.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SS.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

###################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SS.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GS.SS.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.MS.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GS.MS.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.MS.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GS.MS.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

####################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size +Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GS.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

####################
slouch.output<-make.slouch.table(ECV.FoDCS.GS.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories Strict+Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GS.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)



##################
slouch.output<-make.slouch.table(ECV.FoDCS.GSC.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Group Size Categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GSC.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size Categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDCS.GSC.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.GSC.BoM.BM,"FF.BM","Fol Diet Categories Strict+Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
##################
slouch.output<-make.slouch.table(ECV.FoDCS.SS.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.SS.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDCS.SS.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.SS.BoM.BM,"FF.BM","Fol Diet Categories Strict+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDCS.MS.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.MS.AP.BoM.BM,"FF.BM","Fol Diet Categories Strict+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDCS.MS.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.MS.BoM.BM,"FF.BM","Fol Diet Categories Strict+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#############################
slouch.output<-make.slouch.table(ECV.FoDCS.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Stricts+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.AP.BoM.BM,"FF.BM","Fol Diet Categories Stricts+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#Single factors in addition to Body Mass
#############################
slouch.output<-make.slouch.table(ECV.FoDCS.BoM.OUDF,"OU.FF.DE","Fol Diet Categories Strict",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDCS.BoM.BM,"FF.BM","Fol Diet Categories Strict",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

```

Original Folivore Definition based on % Diet
Social System Group Type
```{r}
slouch.output<-make.slouch.table(ECV.FrDC.GS.SSGT.AP.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GS.SSGT.AP.BoM.BM,"FF.BM","Frug Diet Categories+Group Size+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#################

slouch.output<-make.slouch.table(ECV.FrDC.GS.SSGT.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GS.SSGT.BoM.BM,"FF.BM","Frug Diet Categories+Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)



##################
slouch.output<-make.slouch.table(ECV.FrDC.SSGT.AP.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.SSGT.AP.BoM.BM,"FF.BM","Frug Diet Categories+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


##################
slouch.output<-make.slouch.table(ECV.FrDC.SSGT.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.SSGT.BoM.BM,"FF.BM","Frug Diet Categories+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


###################
slouch.output<-make.slouch.table(ECV.FoDC.GS.SSGT.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size+Social System GT+Acivity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.SSGT.AP.BoM.BM,"FF.BM","Fol Diet Categories+Group Size+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


###################
slouch.output<-make.slouch.table(ECV.FoDC.GS.SSGT.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.SSGT.BoM.BM,"FF.BM","Fol Diet Categories+Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


##################
slouch.output<-make.slouch.table(ECV.FoDC.SSGT.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.SSGT.AP.BoM.BM,"FF.BM","Fol Diet Categories+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDC.SSGT.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.SSGT.BoM.BM,"FF.BM","Fol Diet Categories+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.GS.SSGT.AP.BoM.OURDF,"OU.FF.AD.DE","Group Size+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.SSGT.AP.BoM.BM,"FF.BM","Group Size+Social System GT+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.GS.SSGT.BoM.OURDF,"OU.FF.AD.DE","Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.SSGT.BoM.BM,"FF.BM","Group Size+Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#############################
slouch.output<-make.slouch.table(ECV.SSGT.AP.BoM.OUDF,"OU.FF.DE","Social System GTs+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.SSGT.AP.BoM.BM,"FF.BM","Social System GTs+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.SSGT.BoM.OUDF,"OU.FF.DE","Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.SSGT.BoM.BM,"FF.BM","Social System GT",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
```


## Original DeCasien et al. 2017 Sociality Data

```{r}
slouch.output<-make.slouch.table(ECV.FrDC.GS.SS.AP.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

slouch.output<-make.slouch.table(ECV.FrDC.GS.SS.AP.BoM.BM,"FF.BM","Frug Diet Categories+Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#################
slouch.output<-make.slouch.table(ECV.FrDC.GS.SS.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GS.SS.BoM.BM,"FF.BM","Frug Diet Categories+Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#################
slouch.output<-make.slouch.table(ECV.FrDC.GS.MS.AP.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GS.MS.AP.BoM.BM,"FF.BM","Frug Diet Categories+Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#################
slouch.output<-make.slouch.table(ECV.FrDC.GS.MS.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GS.MS.BoM.BM,"FF.BM","Frug Diet Categories+Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

####################
slouch.output<-make.slouch.table(ECV.FrDC.GS.AP.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GS.AP.BoM.BM,"FF.BM","Frug Diet Categories+Group Size+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

####################
slouch.output<-make.slouch.table(ECV.FrDC.GS.BoM.OURDF,"OU.FF.AD.DE","Frug Diet Categories+Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GS.BoM.BM,"FF.BM","Frug Diet Categories+Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


##################
slouch.output<-make.slouch.table(ECV.FrDC.GSC.AP.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Group Size Categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GSC.AP.BoM.BM,"FF.BM","Frug Diet Categories+Group Size Categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FrDC.GSC.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.GSC.BoM.BM,"FF.BM","Frug Diet Categories+Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FrDC.SS.AP.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.SS.AP.BoM.BM,"FF.BM","Frug Diet Categories+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


##################
slouch.output<-make.slouch.table(ECV.FrDC.SS.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.SS.BoM.BM,"FF.BM","Frug Diet Categories+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FrDC.MS.AP.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.MS.AP.BoM.BM,"FF.BM","Frug Diet Categories+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


##################
slouch.output<-make.slouch.table(ECV.FrDC.MS.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.MS.BoM.BM,"FF.BM","Frug Diet Categories+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#Folivore
###################
slouch.output<-make.slouch.table(ECV.FoDC.GS.SS.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.SS.AP.BoM.BM,"FF.BM","Fol Diet Categories+Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


###################
slouch.output<-make.slouch.table(ECV.FoDC.GS.SS.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.SS.BoM.BM,"FF.BM","Fol Diet Categories+Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#################
slouch.output<-make.slouch.table(ECV.FoDC.GS.MS.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.MS.AP.BoM.BM,"FF.BM","Fol Diet Categories+Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#################
slouch.output<-make.slouch.table(ECV.FoDC.GS.MS.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.MS.BoM.BM,"FF.BM","Fol Diet Categories+Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

####################
slouch.output<-make.slouch.table(ECV.FoDC.GS.AP.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.AP.BoM.BM,"FF.BM","Fol Diet Categories+Group Size+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

####################
slouch.output<-make.slouch.table(ECV.FoDC.GS.BoM.OURDF,"OU.FF.AD.DE","Fol Diet Categories+Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GS.BoM.BM,"FF.BM","Fol Diet Categories+Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


##################
slouch.output<-make.slouch.table(ECV.FoDC.GSC.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Group Size Categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GSC.AP.BoM.BM,"FF.BM","Fol Diet Categories+Group Size Categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDC.GSC.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.GSC.BoM.BM,"FF.BM","Fol Diet Categories+Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
##################
slouch.output<-make.slouch.table(ECV.FoDC.SS.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.SS.AP.BoM.BM,"FF.BM","Fol Diet Categories+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDC.SS.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.SS.BoM.BM,"FF.BM","Fol Diet Categories+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDC.MS.AP.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.MS.AP.BoM.BM,"FF.BM","Fol Diet Categories+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.FoDC.MS.BoM.OUDF,"OU.FF.DE","Fol Diet Categories+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.MS.BoM.BM,"FF.BM","Fol Diet Categories+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#################
#End of DIET Interaction

##################
slouch.output<-make.slouch.table(ECV.GS.SS.AP.BoM.OURDF,"OU.FF.AD.DE","Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.SS.AP.BoM.BM,"FF.BM","Group Size+Social System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.GS.SS.BoM.OURDF,"OU.FF.AD.DE","Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.SS.BoM.BM,"FF.BM","Group Size+Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.GS.MS.AP.BoM.OURDF,"OU.FF.AD.DE","Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.MS.AP.BoM.BM,"FF.BM","Group Size+Mating System+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

##################
slouch.output<-make.slouch.table(ECV.GS.MS.BoM.OURDF,"OU.FF.AD.DE","Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.MS.BoM.BM,"FF.BM","Group Size+Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


#Single Factors+AP
#############################
slouch.output<-make.slouch.table(ECV.FrDC.AP.BoM.OUDF,"OU.FF.DE","Frug Diet Categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.AP.BoM.BM,"FF.BM","Frug Diet categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.FoDC.AP.BoM.OUDF,"OU.FF.DE","Fol Diet categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.AP.BoM.BM,"FF.BM","Fol Diet categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.GSC.AP.BoM.OUDF,"OU.FF.DE","Group Size categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GSC.AP.BoM.BM,"FF.BM","Group Size categories+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.SS.AP.BoM.OUDF,"OU.FF.DE","Social Systems+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.SS.AP.BoM.BM,"FF.BM","Social Systems+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.MS.AP.BoM.OUDF,"OU.FF.DE","Mating Systems+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.MS.AP.BoM.BM,"FF.BM","Mating Systems+Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#Single factors in addition to Body Mass
#############################
slouch.output<-make.slouch.table(ECV.FrDC.BoM.OUDF,"OU.FF.DE","Frug Diet Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FrDC.BoM.BM,"FF.BM","Frug Diet Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.FoDC.BoM.OUDF,"OU.FF.DE","Fol Diet Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.FoDC.BoM.BM,"FF.BM","Fol Diet Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.GSC.BoM.OUDF,"OU.FF.DE","Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GSC.BoM.BM,"FF.BM","Group Size Categories",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.SS.BoM.OUDF,"OU.FF.DE","Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.SS.BoM.BM,"FF.BM","Social System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.MS.BoM.OUDF,"OU.FF.DE","Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.MS.BoM.BM,"FF.BM","Mating System",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

#############################
slouch.output<-make.slouch.table(ECV.AP.BoM.OUDF,"OU.FF.DE","Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.AP.BoM.BM,"FF.BM","Activity Pattern",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)



```

```{r}

###########
slouch.output<-make.slouch.table(ECV.GS.BoM.OURD,"OU.AD.DE","Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.GS.BoM.BM,"BM","Group Size",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
###########


slouch.output<-make.slouch.table(ECV.BoM.OU,"OU.DE","Comparison-Body Mass",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.BoM.BM,"BM","Comparison-Body Mass",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

slouch.output<-make.slouch.table(ECV.OU,"OU.NP","ECV~1",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.BM,"BM.NP","ECV~1",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)

slouch.output<-make.slouch.table(BoM.OU,"OU.NP","Body Mass~1",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(BoM.BM,"BM.NP","Body Mass~1",dim(BrBo.Diet.DC.GS.SS.AP.trdata$dat)[1],slouch.output)


slouch.table<-make_regression_table(slouch.output)

```


```{r}
save.image("SBR2 - WS from SIMMAP ACE - All Primates - 128 sp - Scaled 062522.RData")
```


```{r}
write.table(slouch.output,"SBR2_SIMMAPACE_All_Primates_Scaled_Slouch_Table_128sp_062522_hcfalse.csv",sep=",",row.names=FALSE)
write.table(slouch.table,"SBR2_SIMMAPACE_All_Primates_Scaled_AIC_Table_128sp_062522_hcfalse.csv",sep=",",row.names=FALSE)
```

``

 