---
title: "SBR2 - Bayou Shifts Code 042722"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
New Categories based on Masahito's suggestion - Frug/Non-Frug, Fol/Non-Fol - using the % time spent feeding as a resource

All Primates Analysis
```{r}
rm(list=ls())

#devtools::install_github("kopperud/slouch")
#devtools::install_github("liamrevell/phytools")
library(slouch)
library(phytools)

library(treeplyr)
#library(bayou)
library(plyr)
#library(ape)
#library(viridis)
options(scipen=999)
#For execution on a local, multicore CPU with excess RAM we recommend calling
#options(mc.cores = parallel::detectCores())


source('/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.slouch.simmap.table.v1.R')

source('/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.slouch.simmap.AIC.table.R1.v1.R')

source("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.regression.table.R1.R")

source('/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Programs/make.slouch.table.R1.v1.R')


#Pairwise trends
#source('/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/Programs/make.slouch.table.v3.R')

#Taking a portion of the phylogeny and matching up internal nodes
#source("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/Programs/new.internal.regime.assigments.R")

```

Read in all data, including data on brain and body size with measurement error from Grabowski et al. (2016)

```{r}
#Orignal submission tree
#phylo.tree<-read.tree("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/Tree/AAPA_111118_10K.tre")

#SB Revision 1 Tree
phylo.tree<-read.tree("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/Tree/SB_Rv1_10K.tre")

#After renaming family to Callitrichidae - only change
brbo.data<-read.csv("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/ME Data/BrBo_means_predME_10192020_Callitri_tarsiers_step.csv")

diet.data<-read.csv("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/My Diet Data/Primate_Diet_Breakdown_100119.csv")

avg_GS.data<-read.csv("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New Group Size Data/Average.GS.DeCasien.Powell.01232019.csv")

SS.data<-read.csv("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/New Data/New SS Data/DeCasien MG Latest SS 020619.csv")


```

Drop tip for Chiropotes satanas to match original submission sample
```{r}
#which(phylo.tree$tip.label=="Chiropotes_satanas")
#length(phylo.tree$tip.label)
#phylo.tree<-drop.tip(phylo.tree,tip="Chiropotes_satanas")
#length(phylo.tree$tip.label)
```


Rescale to unit length
```{r}
l.tree<-max(branching.times(phylo.tree))
phylo.tree$edge.length<-phylo.tree$edge.length/l.tree ## rescale tree to height 1
max(branching.times(phylo.tree))

```


Get tree length
```{r}
phylo.tree <- multi2di(phylo.tree, random=FALSE)
phylo.tree$edge.length[phylo.tree$edge.length==0] <- .Machine$double.eps

#Reorder tree "postorder" to match bayou
#phylo.tree<-reorder(phylo.tree,order = "postorder")
max(branching.times(phylo.tree))
```


Add on measurement error columns for Brain and Body Size
```{r}
#Brain/Body/Diet Data
brbo.data$N.species

brbo.data<-mutate(brbo.data,me.ECV.species=brbo.data$predict.sp.ln_ECV/brbo.data$N.species)
brbo.data<-mutate(brbo.data,me.BoM.species=brbo.data$predict.sp.ln_Body.mass/brbo.data$N.body.mass.species)

brbo.data<-mutate(brbo.data,me.ECV.females=brbo.data$predict.F.ln_ECV/brbo.data$N.female)
brbo.data<-mutate(brbo.data,me.BoM.females=brbo.data$predict.F.ln_Body.mass/brbo.data$N.body.mass.female)

brbo.data<-mutate(brbo.data,me.ECV.males=brbo.data$predict.M.ln_ECV/brbo.data$N.male)
brbo.data<-mutate(brbo.data,me.BoM.males=brbo.data$predict.M.ln_Body.mass/brbo.data$N.body.mass.male)
```
Split into Haplorhinnes vs. Strepsirrhines
```{r}
#brbo.data<-filter(brbo.data,Suborder=="Haplorrhini")
#brbo.data<-filter(brbo.data,Suborder=="Strepsirrhini")
#brbo.data<-filter(brbo.data,Parvorder=="Catarrhini")
#brbo.data<-filter(brbo.data,Parvorder=="Platyrrhini")

```


Max vy for body mass - add in upper range for vy
```{r}
#3* Variance of logged response is good upper range for vy says Kjetil, but too much in this case
max.vy<-var(log(brbo.data$Body.mass.species.mean),na.rm=TRUE)
max.hl<-max(branching.times(phylo.tree))
```

Diet Data, independently
```{r}
#Frug/Non Frug, Fol/Non Fol Diet Category Data
BrBo.diet.data<-merge(brbo.data,diet.data,by="Genus_Species")
dim(BrBo.diet.data)

BrBo.diet.trdata <- make.treedata(phylo.tree, BrBo.diet.data,name_column="Genus_Species")
BrBo.diet.trdata<-filter(BrBo.diet.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean)&!is.na(Frug.Non.Frug))

dim(BrBo.diet.trdata$dat)

#For original file with non-substuted males/females for species means
BrBo.diet.trdata<-filter(BrBo.diet.trdata, N.male>=1 & N.body.mass.male>=1 & N.female>=1 & N.body.mass.female>=1 & N.species>1 & N.body.mass.species>1)
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,N.species!="NA" & N.body.mass.species!="NA")

#BrBo.diet.trdata<-filter(BrBo.diet.trdata, N.species>=1 & N.body.mass.species>=1)
#BrBo.diet.trdata<-filter(BrBo.diet.trdata,N.species!="NA" & N.body.mass.species!="NA")

dim(BrBo.diet.trdata$dat)

#write.table(BrBo.diet.trdata$dat,"test.csv",sep=",",row.names = FALSE)

```

Setup for Merged Data
Merged Brain/Body + Diet % + DC + GS + SS, n=114
```{r}
BrBo.Diet.GS.data<-merge(BrBo.diet.data,avg_GS.data,by="Genus_Species")
BrBo.Diet.GS.SS.data<-merge(BrBo.Diet.GS.data,SS.data,by="Genus_Species")

dim(BrBo.Diet.GS.SS.data)

BrBo.Diet.DC.GS.SS.trdata <- make.treedata(phylo.tree, BrBo.Diet.GS.SS.data,name_column="Genus_Species")

BrBo.Diet.DC.GS.SS.trdata<-filter(BrBo.Diet.DC.GS.SS.trdata,!is.na(ECV.species.mean)&!is.na(Body.mass.species.mean)&!is.na(Combo.AGS)&!is.na(Social.System)&!is.na(Frug.Non.Frug ))

BrBo.Diet.DC.GS.SS.trdata<-filter(BrBo.Diet.DC.GS.SS.trdata, N.male>=1 & N.body.mass.male>=1 & N.female>=1 & N.body.mass.female>=1 & N.species>1 & N.body.mass.species>1)

#For original file with non-substuted males/females for species means
#BrBo.Diet.DC.GS.SS.trdata<-filter(BrBo.Diet.DC.GS.SS.trdata,N.body.mass.male>=1 & N.body.mass.female>=1)
#BrBo.Diet.DC.GS.SS.trdata<-filter(BrBo.Diet.DC.GS.SS.trdata,N.species!="NA" & N.body.mass.species!="NA")

BrBo.Diet.DC.GS.SS.trdata$dat$Fol.Non.Fol<-revalue(BrBo.Diet.DC.GS.SS.trdata$dat$Fol.Non.Fol,c("Fol"="Folivorous","Non.Fol"="Non"))

BrBo.Diet.DC.GS.SS.trdata$dat$Frug.Non.Frug<-revalue(BrBo.Diet.DC.GS.SS.trdata$dat$Frug.Non.Frug,c("Frug"="Frugivorous","Non.Frug"="Non"))

dim(BrBo.Diet.DC.GS.SS.trdata$dat)

```
Break average group size continuous variable into categories
```{r}
#################
library(ape)

#Group size into 
gs.cat<-cut(BrBo.Diet.DC.GS.SS.trdata$dat$Combo.AGS,
    breaks = c(0,5, 10, 25, 50,Inf), 
    labels = c("1-5","6-10","11-25","26-50",">50"), 
    right = FALSE)

BrBo.Diet.DC.GS.SS.trdata$dat$Cat.group.size<-gs.cat
```

```{r}
max(branching.times(BrBo.Diet.DC.GS.SS.trdata$phy))

source("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/Programs/bayou2slouch.R")

plot(BrBo.Diet.DC.GS.SS.trdata$phy,font=1,cex=0.25,label.offset = 0);
nodelabels(bg="white",cex=0.2,frame="none",adj=c(1,0));
tiplabels(bg="white",cex=0.2,frame="none",adj=c(1,0))

#Send shifts to bayou2slouch for regime assignments
output<-bayou2slouch(BrBo.Diet.DC.GS.SS.trdata,c(128,130,213))
#output<-bayou2slouch(BrBo.Diet.DC.GS.SS.bayou.trdata,c(126,128))

#Haplorrhines w/ shift in platyrrhines
#output<-bayou2slouch(BrBo.Diet.DC.GS.SS.bayou.trdata,c(XX))
#Platyrrhines w/ shift within this group
#output<-bayou2slouch(BrBo.Diet.DC.GS.SS.bayou.trdata,c(XX))

BrBo.Diet.DC.GS.SS.bayou.trdata<-output[[1]]
internal.bayou.shifts<-output[[2]]

bayou.shifts.total<-c(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,internal.bayou.shifts)
num.tips<-length(BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label)

#Num of node we want to change proceeding branch - 208 in this case
#change.node<-208-num.tips
change.node<-213-num.tips

internal.bayou.shifts[change.node]<-"OU2"

#BrBo.Diet.DC.GS.SS.bayou.trdata
```

Test bayou shifts code - does it produce same plot?
```{r}
bayou.shifts.total<-c(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,internal.bayou.shifts)
  edge.regimes <- factor(bayou.shifts.total[BrBo.Diet.DC.GS.SS.bayou.trdata$phy$edge[,2]])
  print(edge.regimes)
  #Get ggplot colors used for plot to make on tree
  gg_color_hue <- function(n) {
    hues = seq(15, 375, length=n+1)
    hcl(h=hues, l=65, c=100)[1:n]
  }
  
  reg.colors<-gg_color_hue(length(unique(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts)))

  print(reg.colors)
  plot(BrBo.Diet.DC.GS.SS.bayou.trdata$phy,edge.color = reg.colors[edge.regimes], edge.width = 1, cex = 0.2)
  



```



```{r}

############
#Group Size
BrBo.Diet.DC.GS.SS.bayou.trdata$phy$node.label <- internal.bayou.shifts

ECV.GS.BoM.OURD<-slouch.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                                     species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                                     response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$ECV.species.mean),
                                     random.cov = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Combo.AGS),
                                     fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                                     direct.cov = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Body.mass.species.mean),
                                     mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.ECV.species,
                                     mv.direct.cov = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.BoM.species,
                                     hl_values = seq(0.00001, max.hl*3, length.out = 50),
                                     vy_values = seq(0.00001, 1, length.out = 50),
                                     hillclimb = FALSE,convergence = 150,
                                     lower = c(0.00001, 0.00001))

summary(ECV.GS.BoM.OURD)


ECV.GS.BoM.BM<-brown.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                                 species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                                 response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$ECV.species.mean),
                                                              fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                                     random.cov = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Combo.AGS),
                                     direct.cov = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Body.mass.species.mean),
                                     mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.ECV.species,
                                     mv.direct.cov = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.BoM.species,
                                 hillclimb = TRUE,convergence = 150,
                                 lower = c(0.00001, 0.00001))

summary(ECV.GS.BoM.BM)


```

```{r}
BrBo.Diet.DC.GS.SS.bayou.trdata$phy$node.label <- internal.bayou.shifts

#OU Model of Evolution
ECV.BoM.OU<-slouch.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Body.mass.species.mean),
                              fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                              mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.BoM.species,
                              hl_values = seq(0.00001, max.hl*3, length.out = 50),
                              vy_values = seq(0.00001, 1, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.00001, 0.00001))

summary(ECV.BoM.OU)


#BM Model of Evolution
ECV.BoM.BM<-brown.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$ECV.species.mean),
                              direct.cov = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Body.mass.species.mean),
                                                    fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                              mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.ECV.species,
                              mv.direct.cov = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.00001, 0.00001))


summary(ECV.BoM.BM)

```

```{r}
#OU Model of Evolution
ECV.OU<-slouch.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$ECV.species.mean),
                              fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                              mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.ECV.species,
                              hl_values = seq(0.00001, max.hl*3, length.out = 50),
                              vy_values = seq(0.00001, 10, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.00001, 0.00001))

summary(ECV.OU)


#BM Model of Evolution
ECV.BM<-brown.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$ECV.species.mean),
                                                fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                              mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.ECV.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.00001, 0.00001))


summary(ECV.BM)

```

```{r}
#OU Model of Evolution
BoM.OU<-slouch.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Body.mass.species.mean),
                                                 fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                              mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.BoM.species,
                              hl_values = seq(0.00001, max.hl*3, length.out = 50),
                              vy_values = seq(0.00001, 10, length.out = 50),
                              hillclimb = FALSE,convergence = 150,
                              lower = c(0.00001, 0.00001))

summary(BoM.OU)


#BM Model of Evolution
BoM.BM<-brown.fit(phy = BrBo.Diet.DC.GS.SS.bayou.trdata$phy,
                              species = BrBo.Diet.DC.GS.SS.bayou.trdata$phy$tip.label,
                              response = log(BrBo.Diet.DC.GS.SS.bayou.trdata$dat$Body.mass.species.mean),
                                                fixed.fact = BrBo.Diet.DC.GS.SS.bayou.trdata$dat$bayou.shifts,

                              mv.response=BrBo.Diet.DC.GS.SS.bayou.trdata$dat$me.BoM.species,
                              hillclimb = TRUE,convergence = 150,
                              lower = c(0.00001, 0.00001))


summary(BoM.BM)

```


```{r}

#Single factors in addition to Body Mass
###########
slouch.output<-make.slouch.table(ECV.GS.BoM.OURD,"OU.AD.DE","Group Size",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1])
slouch.output<-make.slouch.table(ECV.GS.BoM.BM,"BM","Group Size",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1],slouch.output)
####
slouch.output<-make.slouch.table(ECV.BoM.OU,"OU.DE","Comparison-Body Mass",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.BoM.BM,"BM","Comparison-Body Mass",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1],slouch.output)

slouch.output<-make.slouch.table(ECV.OU,"OU.NP","ECV~1",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(ECV.BM,"BM.NP","ECV~1",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1],slouch.output)

slouch.output<-make.slouch.table(BoM.OU,"OU.NP","Body Mass~1",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1],slouch.output)
slouch.output<-make.slouch.table(BoM.BM,"BM.NP","Body Mass~1",dim(BrBo.Diet.DC.GS.SS.bayou.trdata$dat)[1],slouch.output)


slouch.table<-make_regression_table(slouch.output)

```


```{r}
save.image("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/SIMMAP - Constrained/WS from SIMMAP ACE + Bayou Shifts - All Primates - Scaled Slouch 128 sp 081121_hcfalse.RData")
```

```{r}
#load("/Users/markgrabowski/Google Drive/Shared with Mac Pro/Brain Size Diet + Social System/SB Revision 1/WS/Scaled/WS from Ace - All Primates - Scaled Slouch 042721_hcfalse.RData")
```


```{r}
write.table(slouch.output,"SBR1_bayou_shifts_ACE_All_Primates_Scaled_Slouch_Table_082121_hcfalse.csv",sep=",",row.names=FALSE)
write.table(slouch.table,"SBR1_bayou_shifts_ACE_All_Primates_Scaled_AIC_Table_082121_hcfalse.csv",sep=",",row.names=FALSE)


```


